---
title: "Descriptivas EPICO"
author: "Gabriela Friedrich"
date: "8/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr) #Para mejorar calidad de reportes
library(tidyverse) #Manipulacion y visualización de data
library(magrittr) #Manipulación de data
library(kableExtra) #Mejorar calidad de reportes
library(dlookr) #Si no funciona reinstalar "rmarkdown". Para diagnosticos generales
library(lubridate) #Manejo de fechas
library(Hmisc)
library(plotly)
library(summarytools)
opts_chunk$set(results = 'asis',      # Can also be set at the chunk-level
                comment = NA,
                prompt  = FALSE,
                cache   = FALSE, 
               warning = FALSE)
st_options(plain.ascii = FALSE,        # Always use this option in Rmd documents
            style        = "rmarkdown", # Always use this option in Rmd documents
            footnote     = NA,          # Makes html-rendered results more concise
            subtitle.emphasis = FALSE)  # Improves layout with some rmardown themes


#https://cran.r-project.org/web/packages/summarytools/vignettes/Introduction.html
#https://cran.r-project.org/web/packages/qwraps2/vignettes/summary-statistics.html#count-and-percentages
#https://methodenlehre.github.io/SGSCLM-R-course/descriptive-statistics.html
#https://plotly-r.com/arranging-views.html
#https://cran.r-project.org/web/packages/vtable/vignettes/sumtable.html
```


```{r}
# rm(list=ls())
# data=read.csv('C:/Users/gaga1/OneDrive/Documents/MEPI/EPICO/Control de calidad/Datos_Todos__06_2021/EPICOCOLOMBIA_DATA_2021-06-06_2021.csv')
# data=data[,! names(data) %in% ("redcap_data_access_group") ]

rm(list=ls())




data=read.csv('C:/Users/gaga1/OneDrive/Documents/MEPI/EPICO/Control de calidad/Datos_Todos_7_03_2022/EPICOCOLOMBIA_DATA_2022-03-07_1414.csv')
data=data[,! names(data) %in% ("redcap_data_access_group") ]

```

```{r, echo = FALSE}
# #Setting Labels
# 
# label(data$record)="Identification"
# label(data$hospital)="Hospital"
# label(data$health_worker_name)="Who fills the paper data notebook (name)"
# label(data$center_id_complete)="Complete?"
# label(data$patient_birth_date)="Patients date of birth"
# label(data$admission_date)="Date of admission"
# label(data$age_months)="Age in months"
# label(data$sex)="Sex at Birth:"
# label(data$last_15)="Has the child been previously admitted to hospital in the last 15 days?"
# label(data$demographics_complete)="Complete?"
# label(data$symptoms_epi_travel)="A history of travel to an area with documented cases of novel coronavirus infection"
# label(data$symptoms_epi_physical)="Close contact with a confirmed or probable case of nCoV infection"
# label(data$symptoms_epi_healthfac)="Presence in a healthcare facility where nCoV infections have been managed"
# label(data$symptoms_epi_animal)="Direct contact with animals in countries where the nCoV is known to be circulating in animal populations or where human infections have occurred as a result of presumed zoonotic transmission"
# label(data$symptoms_epi_comm)="Area with community transmission"
# label(data$contact___1)="Close contact (choice=Health care associated exposure, including providing direct care for novel coronavirus patients, e.g. health care worker, working with health care workers infected with novel coronavirus, visiting patients or staying in the same close environment of a novel coronavirus patient, or direct exposure to body fluids or specimens including aerosols)"
# label(data$contact___2)="Close contact (choice=Working together in close proximity or sharing the same classroom environment with a novel coronavirus patient)"
# label(data$contact___3)="Close contact (choice=Traveling together with novel coronavirus patient in any kind of conveyance)"
# label(data$contact___4)="Close contact (choice=Living in the same household as a novel coronavirus patient)"
# label(data$index_case)="Who is the index case (father, mother, uncle ...)"
# label(data$inclusion_criteria_complete)="Complete?"
# label(data$fever_start_date)="Fever onset date"
# label(data$fever_days)="Fever days (from start to admission, including start day)"
# label(data$fever_days_total)="Fever days (from start to end, including start day)"
# label(data$fever_3)="Fever days >= 3"
# label(data$anamnesis_complete)="Complete?"
# label(data$comorb)="Comorbidities"
# label(data$chroniccard_mhyn)="Chronic cardiac disease, including congenital heart disease (not hypertesnion)"
# label(data$hypertension_mhyn)="Hypertension"
# label(data$chronicpul_mhyn)="Chronic pulmonary disease (not asthma)"
# label(data$asthma_mhyn)="Asthma (or recurrent wheezing)"
# label(data$tb_mhyn)="Tuberculosis"
# label(data$resp_inf_mhyn)="History of respiratory infection in the previous 4 weeks prior to current illness?"
# label(data$renal_mhyn)="Chronic kidney disease"
# label(data$modliver_mhyn)="Moderate or severe liver disease"
# label(data$mildliv_mhyn)="Mild Liver disease"
# label(data$chronicneu_mhyn)="Chronic neurological disorder"
# label(data$malignantneo_mhyn)="Malignant neoplasm"
# label(data$chronhaemo_mhyn)="Chronic hematologic disease"
# label(data$aidshiv_mhyn)="AIDS/HIV"
# label(data$obesity_mhyn)="Obesity (as defined by clinical staff)"
# label(data$diabetiscomp_mhyn)="Diabetes with complications"
# label(data$diabetes_mhyn)="Diabetes without complications"
# label(data$inflammatory_mhyr)="Inflammatory disorder"
# label(data$rheumatology_mhyr)="Rheumatologic disorder"
# label(data$kawa_mhyn)="Past history of Kawasaki disease"
# label(data$kawa_fam_mhyn)="Family history of Kawasaki disease"
# label(data$dementia_mhyn)="Dementia"
# label(data$malnutrition_mhyn)="Malnutrition"
# label(data$other_mhyn)="Other relevant risk factors"
# label(data$inf_reum_type)="Please specify inflammatory or rheumatological disorder"
# label(data$smoking_mhyn)="Smoking"
# label(data$otherrisktext)="Other  relevant risk factor; Specify"
# label(data$immunosupressors)="On immunosuppressive medication?"
# label(data$comorbidities_complete)="Complete?"
# label(data$influenza_full_regimen)="Influenza vaccine (current year)"
# label(data$apsc_vcageind)="Vaccinations appropriate for age/country?"
# label(data$vaccines_complete)="Complete?"
# label(data$weight)="Weight (grams)"
# label(data$weight_percentile)="Weight percentile"
# label(data$size)="Size (cm)"
# label(data$size_percentile)="Size percentile"
# label(data$anthropometry_complete)="Complete?"
# label(data$temp_vsorres)="Temperature"
# label(data$hr_vsorres)="Heart Rate"
# label(data$rr_vsorres)="Respiratory Rate"
# label(data$sysbp_vsorres)="Systolic blood pressure"
# label(data$admission_diabp_vsorres)="Diastolic blood pressure"
# label(data$oxy_vsorres)="Oxygen saturation"
# label(data$muac)="Mid-upper arm circumference"
# label(data$dehydr)="Dehydratation"
# label(data$fever_ceoccur_v2)="History of fever"
# label(data$cough_ceoccur_v2)="Cough"
# label(data$sorethroat_ceoccur_v2)="Sore throat"
# label(data$runnynose_ceoccur_v2)="Runny nose (Rhinorrhoea)"
# label(data$wheeze_ceoccur_v2)="Wheezing"
# label(data$chestpain_ceoccur_v2)="Chest pain"
# label(data$myalgia_ceoccur_v2)="Muscle aches (Myalgia)"
# label(data$jointpain_ceoccur_v2)="Joint pain (Arthralgia)"
# label(data$fatigue_ceoccur_v2)="Fatigue / Malaise"
# label(data$shortbreath_ceoccur_v2)="Shortness of breath or work of breathing (Dyspnea)"
# label(data$lowerchest_ceoccur_v2)="Lower chest wall indrawing"
# label(data$headache_ceoccur_v2)="Headache"
# label(data$confusion_ceoccur_v2)="Altered consciousness / confusion"
# label(data$seizures_cecoccur_v2)="Seizures"
# label(data$abdopain_ceoccur_v2)="Abdominal pain"
# label(data$vomit_ceoccur_v2)="Vomiting / Nausea"
# label(data$diarrhoea_ceoccur_v2)="Diarrhoea"
# label(data$conjunct_ceoccur_v2)="Conjunctivitis"
# label(data$oral_inf)="Oral mucosal inflammation signs"
# label(data$pale_skin)="Pale/mottled skin"
# label(data$rash_ceoccur_v2)="Skin rash"
# label(data$skinulcers_ceoccur_v2)="Skin ulcers"
# label(data$peri_inf)="Peripheral cutaneous inflammation signs (hands or feet)"
# label(data$lymp_ceoccur_v2)="Lymphadenopathy"
# label(data$bleed_ceoccur_v2)="Bleeding (Haemorrhage)"
# label(data$cold_hands)="Cold hands/feet"
# label(data$cap_refill)="Capillary refill time > 2 seconds ?"
# label(data$sw_joints)="Swollen joints"
# label(data$st_neck)="Stiff neck"
# label(data$hypo_flop)="Hypotonia / floppiness"
# label(data$paralysis)="Paralysis"
# label(data$shock)="Shock signs"
# label(data$sens_alt)="Alteration in taste or smell"
# label(data$admission_signs_and_symptoms_complete)="Complete?"
# label(data$hb)="Hemoglobin"
# label(data$leukocytes)="Leukocytes"
# label(data$neutrophils)="Neutrophils"
# label(data$lymphocytes)="Lymphocytes"
# label(data$platelets)="Platelets"
# label(data$aptt_aptr)="Activated Partial Thromboplastin Time / Ratio (APTT / APTR)"
# label(data$pt)="Prothrombin Time (PT)"
# label(data$inr)="International Normalized Ratio (INR)"
# label(data$fibrino)="Fibrinogen"
# label(data$c_reactive_protein)="C-reactive protein"
# label(data$procalcitonin)="Procalcitonin"
# label(data$cpk)="CPK"
# label(data$alt_gpt)="Alanine aminotransferase-GPT"
# label(data$ast_got)="Aspartate aminotransferase-GOT"
# label(data$urea)="Urea"
# label(data$creatinin)="Creatinine"
# label(data$ldh)="Lactate dehydrogenase"
# label(data$albumin)="Albumin"
# label(data$sodium)="Serum sodium"
# label(data$d_dimer)="Dimer-D"
# label(data$il_6)="IL-6"
# label(data$ferritin)="Ferritin"
# label(data$trig)="Triglycerides"
# label(data$bilirubin)="Total bilirubin"
# label(data$lactate)="Lactate"
# label(data$ph)="pH"
# label(data$po2)="pO2"
# label(data$pco2)="pCO2"
# label(data$blood_tests_complete)="Complete?"
# label(data$pcr_cov2_1)="SARS-CoV-2 PCR at diagnosis"
# label(data$ct_cov2_1)="Cycle threshold (Ct) of SARS-CoV-2 PCR at diagnosis"
# label(data$pcr_cov2_1_date)="Date of SARS-CoV-2 PCR at diagnosis"
# label(data$pcr_cov2_2)="SARS-CoV-2 PCR at visit 2"
# label(data$ct_cov2_2)="Cycle threshold (Ct) of SARS-CoV-2 PCR at visit 2"
# label(data$pcr_cov2_2_date)="Date of SARS-CoV-2 PCR at visit 2"
# label(data$pcr_cov2_3)="SARS-CoV-2 PCR at visit 3"
# label(data$ct_cov2_3)="Cycle threshold (Ct) of SARS-CoV-2 PCR at visit 3"
# label(data$pcr_cov2_3_date)="Date of SARS-CoV-2 PCR at visit 3"
# label(data$pcr_cov2_4)="SARS-CoV-2 PCR at visit 4"
# label(data$ct_cov2_4)="Cycle threshold (Ct) of SARS-CoV-2 PCR at visit 4"
# label(data$pcr_cov2_4_date)="Date of SARS-CoV-2 PCR at visit 4"
# label(data$rapid_ag_test_covid___1)="Rapid Antigenic Test (choice=Nasopharyngeal smear)"
# label(data$rapid_ag_test_covid___2)="Rapid Antigenic Test (choice=Saliva)"
# label(data$rapid_ag_test_covid_1)="Nasopharyngeal smear result"
# label(data$rapid_ag_test_covid_2)="Saliva result"
# label(data$virus_obtained_pcr_16)="PCR obtained for 16 viruses in respiratory secretion"
# label(data$pcr_types_virus_sr___1)="Positive result in respiratory secretion PCR (choice=VRS)"
# label(data$pcr_types_virus_sr___2)="Positive result in respiratory secretion PCR (choice=hMPV)"
# label(data$pcr_types_virus_sr___3)="Positive result in respiratory secretion PCR (choice=PIV 1)"
# label(data$pcr_types_virus_sr___4)="Positive result in respiratory secretion PCR (choice=PIV 2)"
# label(data$pcr_types_virus_sr___5)="Positive result in respiratory secretion PCR (choice=PIV 3)"
# label(data$pcr_types_virus_sr___6)="Positive result in respiratory secretion PCR (choice=PIV 4)"
# label(data$pcr_types_virus_sr___7)="Positive result in respiratory secretion PCR (choice=Influenza A)"
# label(data$pcr_types_virus_sr___8)="Positive result in respiratory secretion PCR (choice=Influenza B)"
# label(data$pcr_types_virus_sr___9)="Positive result in respiratory secretion PCR (choice=hBoV)"
# label(data$pcr_types_virus_sr___10)="Positive result in respiratory secretion PCR (choice=ADV)"
# label(data$pcr_types_virus_sr___11)="Positive result in respiratory secretion PCR (choice=EV-hRV)"
# label(data$pcr_types_virus_sr___12)="Positive result in respiratory secretion PCR (choice=Rhinovirus)"
# label(data$pcr_types_virus_sr___13)="Positive result in respiratory secretion PCR (choice=CoV 229E)"
# label(data$pcr_types_virus_sr___14)="Positive result in respiratory secretion PCR (choice=CoV OC43)"
# label(data$pcr_types_virus_sr___15)="Positive result in respiratory secretion PCR (choice=CoV NL63)"
# label(data$pcr_types_virus_sr___16)="Positive result in respiratory secretion PCR (choice=CoV HKU12)"
# label(data$pcr_atipical_sr)="Obtained PCR sample for atypical respiratory secretion?"
# label(data$pcr_mn_sr)="PCR Mycoplasma pneumoniae in respiratory secretion"
# label(data$pcr_cn_sr)="PCR Chlamydophila pneumoniae in respiratory secretion"
# label(data$pcr_hib_sr)="Haemophilus influenzae PCR in respiratory secretion"
# label(data$pcr_leg_sr)="PCR Legionella in respiratory secretion"
# label(data$pcr_bordetella_sr)="PCR Bordetella in respiratory secretion"
# label(data$anti_influenza)="Antigen Influenza"
# label(data$anti_rsv)="Antigen RSV"
# label(data$res_samples)="Respiratory samples stored?"
# label(data$respiratory_secretion_microbiology_complete)="Complete?"
# label(data$first_sr_sc2)="Acute phase serology SARS-CoV-2 performed"
# label(data$first_sr_sc2_type)="Acute phase serology test"
# label(data$first_sr_sc2_type_ot)="Please, specify other test"
# label(data$first_sr_sc2_date)="Date of acute phase serology SARS-CoV-2"
# label(data$igm_sc2_1)="Acute phase serology IgM SARS-CoV-2"
# label(data$igg_sc2_1)="Acute phase serology IgG SARS-CoV-2"
# label(data$second_sr_sc2)="Follow-up serology SARS-CoV-2 performed"
# label(data$second_sr_sc2_type)="Follow-up serology test"
# label(data$second_sr_sc2_type_ot)="Please, specify other test"
# label(data$second_sr_sc2_date)="Date of follow-up serology SARS-CoV-2"
# label(data$igm_sc2_2)="Follow-up serology IgM SARS-CoV-2"
# label(data$igg_sc2_2)="Follow-up serology IgG SARS-CoV-2"
# label(data$sr_sc2_days)="Days from acute phase and follow-up serology for SARS-COV-2 (including the day when acute phase serology was done)"
# label(data$blood_culture)="Blood culture for significant bacteria"
# label(data$probable_bacterial_etiology_hemoculture)="Most likely bacterial aetiology in blood culture"
# label(data$probable_text)="Please, specify"
# label(data$other_bacteria_hemoculture)="Other bacteria in blood culture"
# label(data$probable_text_2)="Please, specify"
# label(data$first_sr_atipical)="First atypical serology performed"
# label(data$date_ser_1)="Date of first atypical bacteria serology"
# label(data$serology1_igm_mn)="Serology 1 IgM Mycoplasma pneumoniae"
# label(data$serology1_igg_mn)="Serology 1 IgG Mycoplasma pneumoniae"
# label(data$title1_igg_mn)="Title 1 IgG Mycoplasma pneumoniae"
# label(data$serology1_igm_cn)="Serology 1 IgM Chlamydophila pneumoniae"
# label(data$serology1_igg_cn)="Serology 1 IgG Chlamydophila pneumoniae"
# label(data$title1_igg_cn)="Title 1 IgG Chlamydophila pneumoniae"
# label(data$second_sr_atipical)="Second atypical serology performed"
# label(data$date_ser_2)="Date of second atypical bacteria serology"
# label(data$serology2_igm_mn)="Serology 2 IgM Mycoplasma pneumoniae"
# label(data$serology2_igg_mn)="Serology 2 IgG Mycoplasma pneumoniae"
# label(data$title2_igg_mn)="Title 2 IgG Mycoplasma pneumoniae"
# label(data$serology2_igm_cn)="Serology 2 IgM Chlamydophila pneumoniae"
# label(data$serology2_igg_cn)="Serology 2 IgG Chlamydophila pneumoniae"
# label(data$title_igg_mn)="Title 2 IgG Chlamydophila pneumoniae"
# label(data$seroconversion_mn)="Seroconversion"
# label(data$blood_samples)="Whole blood samples stored?"
# label(data$plasma_samples)="Plasma samples stored?"
# label(data$blood_microbiology_complete)="Complete?"
# label(data$codetection)="Codetection"
# label(data$codetecion_type)="Codetection type"
# label(data$codetecion_complete)="Complete?"
# label(data$thoracentesis_done)="Thoracentesis performed"
# label(data$ph_thoracentesis)="pH thoracentesis"
# label(data$ag_pneumo_pf)="Pneumococcal antigen in pleural fluid"
# label(data$pcr_pneumo_pf)="Pleural fluid pneumococcal PCR"
# label(data$culture_pf)="Pleural fluid culture"
# label(data$cultured_bacteria_pf)="Bacteria grown in pleural fluid"
# label(data$other_cultured_bacteria_pf)="Other bacteria in pleural fluid culture"
# label(data$pleural_fluid_microbiology_complete)="Complete?"
# label(data$fever_end_date)="End date of fever"
# label(data$oxygen_therapy)="Oxygen therapy"
# label(data$oxigen_start_date)="Oxygen therapy start date"
# label(data$oxigen_end_date)="End date oxygen therapy"
# label(data$oxygen_therapy_time)="Days of oxygen therapy (including start day)"
# label(data$hft)="High flow therapy"
# label(data$hft_start_date)="High flow start date"
# label(data$hft_end_date)="High flow end date"
# label(data$hft_time)="Days of high flow therapy (including start day)"
# label(data$cpap)="CPAP"
# label(data$cpap_start_date)="CPAP start date"
# label(data$cpap_end_date)="CPAP end date"
# label(data$cpap_time)="Days of CPAP (including start day)"
# label(data$picu_admission)="Admission to PICU"
# label(data$picu_admission_date)="PICU admission date"
# label(data$picu_discharge_date)="PICU discharge date"
# label(data$picu_time)="Days of PICU admission (including admission day)"
# label(data$mechanical_ventilation)="Mechanical ventilation"
# label(data$nimv)="Noninvasive mechanical ventilation"
# label(data$nimv_start_date)="Noninvasive mechanical ventilation start date"
# label(data$nimv_end_date)="Noninvasive mechanical ventilation end date"
# label(data$nimv_time)="Days of noninvasive mechanical ventilation (including start day)"
# label(data$imv)="Invasive mechanical ventilation"
# label(data$imv_start_date)="Invasive mechanical ventilation start date"
# label(data$imv_end_date)="Invasive mechanical ventilation end date"
# label(data$imv_time)="Days of invasive mechanical ventilation (including start day)"
# label(data$discharge_date)="Hospital discharge date"
# label(data$hosp_time)="Days of admission (including admission day)"
# label(data$evolution_complete)="Complete?"
# label(data$complications)="Complications (including new-onset signs or diagnosis after admission, such as Kawasaki-like / Inflammatory Syndrome symptoms)"
# label(data$pleural_effusion)="Pleural effusion"
# label(data$effusion_type)="Type of pleural effusion"
# label(data$corticosteroids)="Systemic corticosteroids"
# label(data$pleural_drainage)="Pleural drainage"
# label(data$drainage_type)="Drain type"
# label(data$pneumatocele_abscess)="Necrotizing pneumonia / abscess / pneumatocele"
# label(data$pneumothorax)="Pneumothorax"
# label(data$cardio_comp)="Cardiological complications"
# label(data$cardio_comp_myoc)="Myocarditis / myocardial dysfunction"
# label(data$cardio_comp_peri)="Pericarditis"
# label(data$cardio_comp_valve)="Valve dysfunction"
# label(data$cardio_comp_arry)="Arrhythmia"
# label(data$cardio_comp_cor)="Coronary abnormalities"
# label(data$cardio_comp_ane)="Aneurysms"
# label(data$cardio_comp_bnp)="NT-proBNP"
# label(data$cardio_comp_trop)="Troponin I"
# label(data$cardio_comp_other)="Other cardiologic complications"
# label(data$sepsis)="Sepsis"
# label(data$renal_failure)="Renal failure"
# label(data$kawa)="Kawasaki-like / Inflammatory Syndrome symptoms"
# label(data$other_complications)="Other complications"
# label(data$complications_complete)="Complete?"
# label(data$x_ray_1)="X-ray 1 image"
# label(data$x_ray_1_date)="Date of X-ray 1"
# label(data$xray_result_1)="Interpretation of first radiological image"
# label(data$x_ray_1_reported_by___1)="Responsible for first radiological image interpretation (choice=Clinician)"
# label(data$x_ray_1_reported_by___2)="Responsible for first radiological image interpretation (choice=Radiology report)"
# label(data$x_ray_1_reported_by___3)="Responsible for first radiological image interpretation (choice=Researcher)"
# label(data$x_ray_1_result_ext)="First radiological image read by external researcher not involved with the patient"
# label(data$x_ray_2)="X-ray 2 image"
# label(data$x_ray_2_date)="Date of X-ray 2"
# label(data$xray_result_2)="Interpretation of second radiological image"
# label(data$x_ray_2_reported_by___1)="Responsible for second radiological image interpretation (choice=Clinician)"
# label(data$x_ray_2_reported_by___2)="Responsible for second radiological image interpretation (choice=Radiology report)"
# label(data$x_ray_2_reported_by___3)="Responsible for second radiological image interpretation (choice=Researcher)"
# label(data$x_ray_2_result_ext)="Second radiological image read by external researcher not involved with the patient"
# label(data$x_ray_3)="X-ray 3 image"
# label(data$x_ray_3_date)="Date of X-ray 3"
# label(data$xray_result_3)="Interpretation of third radiological image"
# label(data$x_ray_3_reported_by___1)="Responsible for third radiological image interpretation (choice=Clinician)"
# label(data$x_ray_3_reported_by___2)="Responsible for third radiological image interpretation (choice=Radiology report)"
# label(data$x_ray_3_reported_by___3)="Responsible for third radiological image interpretation (choice=Researcher)"
# label(data$x_ray_3_result_ext)="Third radiological image read by external researcher not involved with the patient"
# label(data$lung_ct)="Lung CT scan image"
# label(data$lung_ct_date)="Date of Lung CT scan image"
# label(data$cardiac_img)="Cardiac imaging performed?"
# label(data$card_img_results)="Please, specify name of technique and findings"
# label(data$radiology_complete)="Complete?"
# label(data$oro_fluids)="Oral/orogastric fluids?"
# label(data$iv_fluids)="Intravenous fluids?"
# label(data$antiviral_cmyn)="Antiviral agent"
# label(data$antiviral_cmtrt___1)="Specify antiviral agent (choice=Ribavirin)"
# label(data$antiviral_cmtrt___2)="Specify antiviral agent (choice=Lopinavir/Ritonavir)"
# label(data$antiviral_cmtrt___3)="Specify antiviral agent (choice=Interferon-alpha)"
# label(data$antiviral_cmtrt___4)="Specify antiviral agent (choice=Interferon-beta)"
# label(data$antiviral_cmtrt___5)="Specify antiviral agent (choice=Neuraminidase inhibitors)"
# label(data$antiviral_cmtrt___6)="Specify antiviral agent (choice=Remdesivir)"
# label(data$antiviral_cmtrt___7)="Specify antiviral agent (choice=Chloroquine)"
# label(data$antiviral_cmtrt___8)="Specify antiviral agent (choice=Hydroxychloroquine)"
# label(data$antiviral_cmtrt___10)="Specify antiviral agent (choice=Anakinra)"
# label(data$antiviral_cmtrt___11)="Specify antiviral agent (choice=Ivermectin)"
# label(data$antiviral_cmtrt___9)="Specify antiviral agent (choice=Other)"
# label(data$antiviral_cmtype)="Specify other antiviral type"
# label(data$antiviral_days)="Days with antiviral"
# label(data$antibiotic_cmyn)="Antibiotic"
# label(data$iv_ab)="Intravenous antibiotic"
# label(data$type_iv_ab___0)="Type of intravenous antibiotic (choice=Ampicillin)"
# label(data$type_iv_ab___1)="Type of intravenous antibiotic (choice=Cefotaxime)"
# label(data$type_iv_ab___2)="Type of intravenous antibiotic (choice=Cefuroxime)"
# label(data$type_iv_ab___3)="Type of intravenous antibiotic (choice=Vancomycin)"
# label(data$type_iv_ab___4)="Type of intravenous antibiotic (choice=Meropenem)"
# label(data$type_iv_ab___5)="Type of intravenous antibiotic (choice=Clindamycin)"
# label(data$type_iv_ab___6)="Type of intravenous antibiotic (choice=Cefazolin)"
# label(data$type_iv_ab___9)="Type of intravenous antibiotic (choice=Ceftriaxone)"
# label(data$type_iv_ab___8)="Type of intravenous antibiotic (choice=Clavulanic acid)"
# label(data$type_iv_ab___7)="Type of intravenous antibiotic (choice=Other (specify))"
# label(data$other_iv_ab)="Other intravenous antibiotic"
# label(data$iv_ab_start_date)="Intravenous antibiotic start date"
# label(data$iv_ab_end_date)="Intravenous antibiotic end date"
# label(data$iv_ab_days)="Days of intravenous antibiotic (including start date)"
# label(data$o_ab)="Intrahospital oral antibiotic "
# label(data$type_o_ab___1)="Oral antibiotic type (choice=Amoxicillin)"
# label(data$type_o_ab___2)="Oral antibiotic type (choice=Amoxicillin-Clavulanic)"
# label(data$type_o_ab___3)="Oral antibiotic type (choice=Cefuroxime)"
# label(data$type_o_ab___4)="Oral antibiotic type (choice=Azithromycin)"
# label(data$type_o_ab___5)="Oral antibiotic type (choice=Erythromycin)"
# label(data$type_o_ab___6)="Oral antibiotic type (choice=Clindamycin)"
# label(data$type_o_ab___7)="Oral antibiotic type (choice=Cefadroxil)"
# label(data$type_o_ab___8)="Oral antibiotic type (choice=Other (specify))"
# label(data$other_o_ab)="Other oral antibiotic"
# label(data$o_ab_start_date)="Oral antibiotic start date"
# label(data$o_ab_end_date)="Oral antibiotic end date"
# label(data$o_ab_days)="Days of oral antibiotic (including start date)"
# label(data$azithromycin_or_erythromycin)="Oral Azithromycin or Erythromycin"
# label(data$azithromycin_or_erythromycin_2d)="Oral Azithromycin or Erythromycin (during the first 2 days, 36h)"
# label(data$corticost_cmyn)="Corticosteroids"
# label(data$corticost_cmtrt)="Specify corticosteroid type"
# label(data$corticost_cmdose)="Specify corticosteroid dose"
# label(data$corticost_cmroute)="Specify corticosteroid route"
# label(data$anti_inflammatory___1)="Anti-inflammatory treatment (choice=Ibuprofen)"
# label(data$anti_inflammatory___2)="Anti-inflammatory treatment (choice=Tocilizumab)"
# label(data$other_anti_inflammatory)="Other non-Steroidal Anti-Inflammatory Drugs (NSAIDs)"
# label(data$other_anti_inflammatory_type)="Please, specify name of other NSAIDs"
# label(data$iv_imglob)="Intravenous immune globulin"
# label(data$iv_imglob_dose)="Daily intravenous immune globulin dose"
# label(data$iv_imglob_days)="Days of intravenous immune globulin treatment"
# label(data$imod)="Immunomodulators"
# label(data$imod_type)="Please, specify name of immunomodulator"
# label(data$sys_anticoag)="Systemic anticoagulation"
# label(data$sys_anticoag_type)="Please, specify name of systemic anticoagulation agent"
# label(data$anti_mal)="Antimalarial agent"
# label(data$anti_mal_type)="Please, specify name of antimalarial agent"
# label(data$antifung_cmyn)="Antifungal agent"
# label(data$antifung_type)="Please, specify name of antifungal agent"
# label(data$experimental)="Experimental agent"
# label(data$experimental_type)="Please, specify name of experimental agent"
# label(data$other_sc2_treatments)="Other medicationsÂ directed to cure COVID-19"
# label(data$other_sc2_treatments_text)="Please, specify other COVID-19 treatments"
# label(data$vasopressors)="Inotropes/vasopressors"
# label(data$vasopressors_type___1)="Please, specify name of inotropes/vasopressors (choice=Adrenalin)"
# label(data$vasopressors_type___2)="Please, specify name of inotropes/vasopressors (choice=Noradrenaline)"
# label(data$vasopressors_type___3)="Please, specify name of inotropes/vasopressors (choice=Dopamine)"
# label(data$vasopressors_type___4)="Please, specify name of inotropes/vasopressors (choice=Dobutamine)"
# label(data$vasopressors_type___5)="Please, specify name of inotropes/vasopressors (choice=Milrinone)"
# label(data$vasopressors_type___6)="Please, specify name of inotropes/vasopressors (choice=Other (please, specify in comments))"
# label(data$ecmo)="Extracorporeal (ECMO) support"
# label(data$blood_trans)="Blood transfusion"
# label(data$medication_complete)="Complete?"
# label(data$dsterm)="Patient outcome"
# label(data$dsterm_other_text)="Please, specify which facility has been transferred to"
# label(data$excluded_reason)="Reason for exclusion"
# label(data$excluded_reason_ot)="Please specify reason for exclusion"
# label(data$final_dx_global_concept)="Final diagnosis, ICD-10-CM concept/s"
# label(data$final_dx_global_code)="Final diagnosis, ICD-10-CM code/s"
# label(data$final_dx_1)="Primary diagnosis related with COVID-19"
# label(data$related_1)="Is the primary diagnosis related to COVID-19?"
# label(data$final_dx_2)="Secondary diagnosis: comorbidity which conditioned this admission"
# label(data$related_2)="Is the secondary diagnosis related to COVID-19?"
# label(data$final_dx_3)="Other diagnosis"
# label(data$final_dx_4)="Other diagnosis"
# label(data$final_dx_5)="Other diagnosis"
# label(data$final_dx_6)="Other diagnosis"
# label(data$related_3)="Is the other diagnosis related to COVID-19?"
# label(data$outcome_complete)="Complete?"
# label(data$fvc_6m)="Forced vital capacity (FVC)"
# label(data$fev1_6m)="Forced expiratory volume (FEV1)"
# label(data$esp_ave_flux_6m)="Average expiratory flow"
# label(data$spirometry_complete)="Complete?"
# label(data$fever_ws)="Fever without source at emergency ward admission"
# label(data$lumbar_punc)="Lumbar puncture performed"
# label(data$csf_bacteria)="CSF bacterial culture"
# label(data$csf_baceria_type)="Bacteria isolated in CSF"
# label(data$csf_vhs)="CSF VHS PCR "
# label(data$csf_enterovirus)="CSF Enterovirus PCR "
# label(data$csf_sarscov2)="CSF SARSCoV2 PCR "
# label(data$csf_leuco)="Leucocytes in CSF"
# label(data$csf_neutro)="Percentage of Neutrophils CSF"
# label(data$csf_lympho)="Percentage of Lymphocytes in CSF"
# label(data$protein_csf)="Protein in CSF"
# label(data$glucose_csf)="Glucose in CSF"
# label(data$urine_collection)="Urine collection method"
# label(data$urine_dipstik)="Urine dipstick"
# label(data$urine_culture)="Urine culture"
# label(data$bacteria_urine)="Bacteria isolated in urine "
# label(data$final_diagnosis)="Final diagnosis after fever without source episode, ICD-10-CM concept"
# label(data$final_diagnosis_icd10)="Final diagnosis after fever without source episode, ICD-10-CM code"
# label(data$comments_fws)="Comments"
# label(data$fever_without_source_study_complete)="Complete?"
# label(data$qc_stage)="Current stage of quality control"
# label(data$qc_date)="Date of quality control stage change"
# label(data$first_analysis)="First Analysis"
# label(data$quality_control_complete)="Complete?"

# #Setting Units
# 
# #Setting Factors(will create new variable for factors - cambiar a que no cree nuevas variables)
# data$hospital = factor(data$hospital,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","15"))
# data$center_id_complete = factor(data$center_id_complete,levels=c("0","1","2"))
# data$sex = factor(data$sex,levels=c("1","2","3"))
# data$last_15 = factor(data$last_15,levels=c("1","2","3"))
# data$demographics_complete = factor(data$demographics_complete,levels=c("0","1","2"))
# data$symptoms_epi_travel = factor(data$symptoms_epi_travel,levels=c("1","2","3"))
# data$symptoms_epi_physical = factor(data$symptoms_epi_physical,levels=c("1","2","3"))
# data$symptoms_epi_healthfac = factor(data$symptoms_epi_healthfac,levels=c("1","2","3"))
# data$symptoms_epi_animal = factor(data$symptoms_epi_animal,levels=c("1","2","3"))
# data$symptoms_epi_comm = factor(data$symptoms_epi_comm,levels=c("1","2","3"))
# data$contact___1 = factor(data$contact___1,levels=c("0","1"))
# data$contact___2 = factor(data$contact___2,levels=c("0","1"))
# data$contact___3 = factor(data$contact___3,levels=c("0","1"))
# data$contact___4 = factor(data$contact___4,levels=c("0","1"))
# data$inclusion_criteria_complete = factor(data$inclusion_criteria_complete,levels=c("0","1","2"))
# data$anamnesis_complete = factor(data$anamnesis_complete,levels=c("0","1","2"))
# data$comorb = factor(data$comorb,levels=c("1","0"))
# data$chroniccard_mhyn = factor(data$chroniccard_mhyn,levels=c("1","2","3"))
# data$hypertension_mhyn = factor(data$hypertension_mhyn,levels=c("1","2","3"))
# data$chronicpul_mhyn = factor(data$chronicpul_mhyn,levels=c("1","2","3"))
# data$asthma_mhyn = factor(data$asthma_mhyn,levels=c("1","2","3"))
# data$tb_mhyn = factor(data$tb_mhyn,levels=c("1","2","3"))
# data$resp_inf_mhyn = factor(data$resp_inf_mhyn,levels=c("1","2","3"))
# data$renal_mhyn = factor(data$renal_mhyn,levels=c("1","2","3"))
# data$modliver_mhyn = factor(data$modliver_mhyn,levels=c("1","2","3"))
# data$mildliv_mhyn = factor(data$mildliv_mhyn,levels=c("1","2","3"))
# data$chronicneu_mhyn = factor(data$chronicneu_mhyn,levels=c("1","2","3"))
# data$malignantneo_mhyn = factor(data$malignantneo_mhyn,levels=c("1","2","3"))
# data$chronhaemo_mhyn = factor(data$chronhaemo_mhyn,levels=c("1","2","3"))
# data$aidshiv_mhyn = factor(data$aidshiv_mhyn,levels=c("1","2","3"))
# data$obesity_mhyn = factor(data$obesity_mhyn,levels=c("1","2","3"))
# data$diabetiscomp_mhyn = factor(data$diabetiscomp_mhyn,levels=c("1","2","3"))
# data$diabetes_mhyn = factor(data$diabetes_mhyn,levels=c("1","2","3"))
# data$inflammatory_mhyr = factor(data$inflammatory_mhyr,levels=c("1","2","3"))
# data$rheumatology_mhyr = factor(data$rheumatology_mhyr,levels=c("1","2","3"))
# data$kawa_mhyn = factor(data$kawa_mhyn,levels=c("1","2","3"))
# data$kawa_fam_mhyn = factor(data$kawa_fam_mhyn,levels=c("1","2","3"))
# data$dementia_mhyn = factor(data$dementia_mhyn,levels=c("1","2","3"))
# data$malnutrition_mhyn = factor(data$malnutrition_mhyn,levels=c("1","2","3"))
# data$other_mhyn = factor(data$other_mhyn,levels=c("1","2","3"))
# data$smoking_mhyn = factor(data$smoking_mhyn,levels=c("1","2","3"))
# data$immunosupressors = factor(data$immunosupressors,levels=c("1","0"))
# data$comorbidities_complete = factor(data$comorbidities_complete,levels=c("0","1","2"))
# data$influenza_full_regimen = factor(data$influenza_full_regimen,levels=c("1","0"))
# data$apsc_vcageind = factor(data$apsc_vcageind,levels=c("1","2","3"))
# data$vaccines_complete = factor(data$vaccines_complete,levels=c("0","1","2"))
# data$anthropometry_complete = factor(data$anthropometry_complete,levels=c("0","1","2"))
# data$dehydr = factor(data$dehydr,levels=c("1","2","3"))
# data$fever_ceoccur_v2 = factor(data$fever_ceoccur_v2,levels=c("1","2","3"))
# data$cough_ceoccur_v2 = factor(data$cough_ceoccur_v2,levels=c("1","2","3"))
# data$sorethroat_ceoccur_v2 = factor(data$sorethroat_ceoccur_v2,levels=c("1","2","3"))
# data$runnynose_ceoccur_v2 = factor(data$runnynose_ceoccur_v2,levels=c("1","2","3"))
# data$wheeze_ceoccur_v2 = factor(data$wheeze_ceoccur_v2,levels=c("1","2","3"))
# data$chestpain_ceoccur_v2 = factor(data$chestpain_ceoccur_v2,levels=c("1","2","3"))
# data$myalgia_ceoccur_v2 = factor(data$myalgia_ceoccur_v2,levels=c("1","2","3"))
# data$jointpain_ceoccur_v2 = factor(data$jointpain_ceoccur_v2,levels=c("1","2","3"))
# data$fatigue_ceoccur_v2 = factor(data$fatigue_ceoccur_v2,levels=c("1","2","3"))
# data$shortbreath_ceoccur_v2 = factor(data$shortbreath_ceoccur_v2,levels=c("1","2","3"))
# data$lowerchest_ceoccur_v2 = factor(data$lowerchest_ceoccur_v2,levels=c("1","2","3"))
# data$headache_ceoccur_v2 = factor(data$headache_ceoccur_v2,levels=c("1","2","3"))
# data$confusion_ceoccur_v2 = factor(data$confusion_ceoccur_v2,levels=c("1","2","3"))
# data$seizures_cecoccur_v2 = factor(data$seizures_cecoccur_v2,levels=c("1","2","3"))
# data$abdopain_ceoccur_v2 = factor(data$abdopain_ceoccur_v2,levels=c("1","2","3"))
# data$vomit_ceoccur_v2 = factor(data$vomit_ceoccur_v2,levels=c("1","2","3"))
# data$diarrhoea_ceoccur_v2 = factor(data$diarrhoea_ceoccur_v2,levels=c("1","2","3"))
# data$conjunct_ceoccur_v2 = factor(data$conjunct_ceoccur_v2,levels=c("1","2","3"))
# data$oral_inf = factor(data$oral_inf,levels=c("1","2","3"))
# data$pale_skin = factor(data$pale_skin,levels=c("1","2","3"))
# data$rash_ceoccur_v2 = factor(data$rash_ceoccur_v2,levels=c("1","2","3"))
# data$skinulcers_ceoccur_v2 = factor(data$skinulcers_ceoccur_v2,levels=c("1","2","3"))
# data$peri_inf = factor(data$peri_inf,levels=c("1","2","3"))
# data$lymp_ceoccur_v2 = factor(data$lymp_ceoccur_v2,levels=c("1","2","3"))
# data$bleed_ceoccur_v2 = factor(data$bleed_ceoccur_v2,levels=c("1","2","3"))
# data$cold_hands = factor(data$cold_hands,levels=c("1","2","3"))
# data$cap_refill = factor(data$cap_refill,levels=c("1","2","3"))
# data$sw_joints = factor(data$sw_joints,levels=c("1","2","3"))
# data$st_neck = factor(data$st_neck,levels=c("1","2","3"))
# data$hypo_flop = factor(data$hypo_flop,levels=c("1","2","3"))
# data$paralysis = factor(data$paralysis,levels=c("1","2","3"))
# data$shock = factor(data$shock,levels=c("1","2","3"))
# data$sens_alt = factor(data$sens_alt,levels=c("1","2","3"))
# data$admission_signs_and_symptoms_complete = factor(data$admission_signs_and_symptoms_complete,levels=c("0","1","2"))
# data$blood_tests_complete = factor(data$blood_tests_complete,levels=c("0","1","2"))
# data$pcr_cov2_1 = factor(data$pcr_cov2_1,levels=c("1","2","3","4"))
# data$pcr_cov2_2 = factor(data$pcr_cov2_2,levels=c("1","2","3","4"))
# data$pcr_cov2_3 = factor(data$pcr_cov2_3,levels=c("1","2","3","4"))
# data$pcr_cov2_4 = factor(data$pcr_cov2_4,levels=c("1","2","3","4"))
# data$rapid_ag_test_covid___1 = factor(data$rapid_ag_test_covid___1,levels=c("0","1"))
# data$rapid_ag_test_covid___2 = factor(data$rapid_ag_test_covid___2,levels=c("0","1"))
# data$rapid_ag_test_covid_1 = factor(data$rapid_ag_test_covid_1,levels=c("1","2"))
# data$rapid_ag_test_covid_2 = factor(data$rapid_ag_test_covid_2,levels=c("1","2"))
# data$virus_obtained_pcr_16 = factor(data$virus_obtained_pcr_16,levels=c("1","0"))
# data$pcr_types_virus_sr___1 = factor(data$pcr_types_virus_sr___1,levels=c("0","1"))
# data$pcr_types_virus_sr___2 = factor(data$pcr_types_virus_sr___2,levels=c("0","1"))
# data$pcr_types_virus_sr___3 = factor(data$pcr_types_virus_sr___3,levels=c("0","1"))
# data$pcr_types_virus_sr___4 = factor(data$pcr_types_virus_sr___4,levels=c("0","1"))
# data$pcr_types_virus_sr___5 = factor(data$pcr_types_virus_sr___5,levels=c("0","1"))
# data$pcr_types_virus_sr___6 = factor(data$pcr_types_virus_sr___6,levels=c("0","1"))
# data$pcr_types_virus_sr___7 = factor(data$pcr_types_virus_sr___7,levels=c("0","1"))
# data$pcr_types_virus_sr___8 = factor(data$pcr_types_virus_sr___8,levels=c("0","1"))
# data$pcr_types_virus_sr___9 = factor(data$pcr_types_virus_sr___9,levels=c("0","1"))
# data$pcr_types_virus_sr___10 = factor(data$pcr_types_virus_sr___10,levels=c("0","1"))
# data$pcr_types_virus_sr___11 = factor(data$pcr_types_virus_sr___11,levels=c("0","1"))
# data$pcr_types_virus_sr___12 = factor(data$pcr_types_virus_sr___12,levels=c("0","1"))
# data$pcr_types_virus_sr___13 = factor(data$pcr_types_virus_sr___13,levels=c("0","1"))
# data$pcr_types_virus_sr___14 = factor(data$pcr_types_virus_sr___14,levels=c("0","1"))
# data$pcr_types_virus_sr___15 = factor(data$pcr_types_virus_sr___15,levels=c("0","1"))
# data$pcr_types_virus_sr___16 = factor(data$pcr_types_virus_sr___16,levels=c("0","1"))
# data$pcr_atipical_sr = factor(data$pcr_atipical_sr,levels=c("1","0"))
# data$pcr_mn_sr = factor(data$pcr_mn_sr,levels=c("1","2","3","4"))
# data$pcr_cn_sr = factor(data$pcr_cn_sr,levels=c("1","2","3","4"))
# data$pcr_hib_sr = factor(data$pcr_hib_sr,levels=c("1","2","3","4"))
# data$pcr_leg_sr = factor(data$pcr_leg_sr,levels=c("1","2","3","4"))
# data$pcr_bordetella_sr = factor(data$pcr_bordetella_sr,levels=c("1","2","3","4"))
# data$anti_influenza = factor(data$anti_influenza,levels=c("1","2","3"))
# data$anti_rsv = factor(data$anti_rsv,levels=c("1","2","3"))
# data$res_samples = factor(data$res_samples,levels=c("1","0"))
# data$respiratory_secretion_microbiology_complete = factor(data$respiratory_secretion_microbiology_complete,levels=c("0","1","2"))
# data$first_sr_sc2 = factor(data$first_sr_sc2,levels=c("1","0","2","3"))
# data$first_sr_sc2_type = factor(data$first_sr_sc2_type,levels=c("1","2","3","4"))
# data$igm_sc2_1 = factor(data$igm_sc2_1,levels=c("1","2","3","4"))
# data$igg_sc2_1 = factor(data$igg_sc2_1,levels=c("1","2","3","4"))
# data$second_sr_sc2 = factor(data$second_sr_sc2,levels=c("1","0","2","3"))
# data$second_sr_sc2_type = factor(data$second_sr_sc2_type,levels=c("1","2","3","4"))
# data$igm_sc2_2 = factor(data$igm_sc2_2,levels=c("1","2","3","4"))
# data$igg_sc2_2 = factor(data$igg_sc2_2,levels=c("1","2","3","4"))
# data$blood_culture = factor(data$blood_culture,levels=c("1","0"))
# data$probable_bacterial_etiology_hemoculture = factor(data$probable_bacterial_etiology_hemoculture,levels=c("1","2","3","4"))
# data$other_bacteria_hemoculture = factor(data$other_bacteria_hemoculture,levels=c("1","0"))
# data$first_sr_atipical = factor(data$first_sr_atipical,levels=c("1","0","2","3"))
# data$serology1_igm_mn = factor(data$serology1_igm_mn,levels=c("1","2","3","4"))
# data$serology1_igg_mn = factor(data$serology1_igg_mn,levels=c("1","2","3","4"))
# data$serology1_igm_cn = factor(data$serology1_igm_cn,levels=c("1","2","3","4"))
# data$serology1_igg_cn = factor(data$serology1_igg_cn,levels=c("1","2","3","4"))
# data$second_sr_atipical = factor(data$second_sr_atipical,levels=c("1","0","2","3"))
# data$serology2_igm_mn = factor(data$serology2_igm_mn,levels=c("1","2","3","4"))
# data$serology2_igg_mn = factor(data$serology2_igg_mn,levels=c("1","2","3","4"))
# data$serology2_igm_cn = factor(data$serology2_igm_cn,levels=c("1","2","3","4"))
# data$serology2_igg_cn = factor(data$serology2_igg_cn,levels=c("1","2","3","4"))
# data$seroconversion_mn = factor(data$seroconversion_mn,levels=c("1","2","3","4"))
# data$blood_samples = factor(data$blood_samples,levels=c("1","0"))
# data$plasma_samples = factor(data$plasma_samples,levels=c("1","0"))
# data$blood_microbiology_complete = factor(data$blood_microbiology_complete,levels=c("0","1","2"))
# data$codetection = factor(data$codetection,levels=c("1","2","3","4"))
# data$codetecion_type = factor(data$codetecion_type,levels=c("1","2"))
# data$codetecion_complete = factor(data$codetecion_complete,levels=c("0","1","2"))
# data$thoracentesis_done = factor(data$thoracentesis_done,levels=c("1","0"))
# data$ag_pneumo_pf = factor(data$ag_pneumo_pf,levels=c("1","2","3"))
# data$pcr_pneumo_pf = factor(data$pcr_pneumo_pf,levels=c("1","2","3"))
# data$culture_pf = factor(data$culture_pf,levels=c("1","2"))
# data$cultured_bacteria_pf = factor(data$cultured_bacteria_pf,levels=c("1","2","3","4","5"))
# data$pleural_fluid_microbiology_complete = factor(data$pleural_fluid_microbiology_complete,levels=c("0","1","2"))
# data$oxygen_therapy = factor(data$oxygen_therapy,levels=c("1","0"))
# data$hft = factor(data$hft,levels=c("1","0"))
# data$cpap = factor(data$cpap,levels=c("1","0"))
# data$picu_admission = factor(data$picu_admission,levels=c("1","0"))
# data$mechanical_ventilation = factor(data$mechanical_ventilation,levels=c("1","0"))
# data$nimv = factor(data$nimv,levels=c("1","0"))
# data$imv = factor(data$imv,levels=c("1","0"))
# data$evolution_complete = factor(data$evolution_complete,levels=c("0","1","2"))
# data$complications = factor(data$complications,levels=c("1","0"))
# data$pleural_effusion = factor(data$pleural_effusion,levels=c("1","0"))
# data$effusion_type = factor(data$effusion_type,levels=c("1","2"))
# data$corticosteroids = factor(data$corticosteroids,levels=c("1","0"))
# data$pleural_drainage = factor(data$pleural_drainage,levels=c("1","0"))
# data$drainage_type = factor(data$drainage_type,levels=c("1","2","3"))
# data$pneumatocele_abscess = factor(data$pneumatocele_abscess,levels=c("1","0"))
# data$pneumothorax = factor(data$pneumothorax,levels=c("1","0"))
# data$cardio_comp = factor(data$cardio_comp,levels=c("1","0"))
# data$cardio_comp_myoc = factor(data$cardio_comp_myoc,levels=c("1","0"))
# data$cardio_comp_peri = factor(data$cardio_comp_peri,levels=c("1","0"))
# data$cardio_comp_valve = factor(data$cardio_comp_valve,levels=c("1","0"))
# data$cardio_comp_arry = factor(data$cardio_comp_arry,levels=c("1","0"))
# data$cardio_comp_cor = factor(data$cardio_comp_cor,levels=c("1","0"))
# data$cardio_comp_ane = factor(data$cardio_comp_ane,levels=c("1","0"))
# data$sepsis = factor(data$sepsis,levels=c("1","0"))
# data$renal_failure = factor(data$renal_failure,levels=c("1","0"))
# data$kawa = factor(data$kawa,levels=c("1","0"))
# data$complications_complete = factor(data$complications_complete,levels=c("0","1","2"))
# data$xray_result_1 = factor(data$xray_result_1,levels=c("1","2","3"))
# data$x_ray_1_reported_by___1 = factor(data$x_ray_1_reported_by___1,levels=c("0","1"))
# data$x_ray_1_reported_by___2 = factor(data$x_ray_1_reported_by___2,levels=c("0","1"))
# data$x_ray_1_reported_by___3 = factor(data$x_ray_1_reported_by___3,levels=c("0","1"))
# data$x_ray_1_result_ext = factor(data$x_ray_1_result_ext,levels=c("1","2","3"))
# data$xray_result_2 = factor(data$xray_result_2,levels=c("1","2","3"))
# data$x_ray_2_reported_by___1 = factor(data$x_ray_2_reported_by___1,levels=c("0","1"))
# data$x_ray_2_reported_by___2 = factor(data$x_ray_2_reported_by___2,levels=c("0","1"))
# data$x_ray_2_reported_by___3 = factor(data$x_ray_2_reported_by___3,levels=c("0","1"))
# data$x_ray_2_result_ext = factor(data$x_ray_2_result_ext,levels=c("1","2","3"))
# data$xray_result_3 = factor(data$xray_result_3,levels=c("1","2","3"))
# data$x_ray_3_reported_by___1 = factor(data$x_ray_3_reported_by___1,levels=c("0","1"))
# data$x_ray_3_reported_by___2 = factor(data$x_ray_3_reported_by___2,levels=c("0","1"))
# data$x_ray_3_reported_by___3 = factor(data$x_ray_3_reported_by___3,levels=c("0","1"))
# data$x_ray_3_result_ext = factor(data$x_ray_3_result_ext,levels=c("1","2","3"))
# data$cardiac_img = factor(data$cardiac_img,levels=c("1","2","3"))
# data$radiology_complete = factor(data$radiology_complete,levels=c("0","1","2"))
# data$oro_fluids = factor(data$oro_fluids,levels=c("1","2","3"))
# data$iv_fluids = factor(data$iv_fluids,levels=c("1","2","3"))
# data$antiviral_cmyn = factor(data$antiviral_cmyn,levels=c("1","2","3"))
# data$antiviral_cmtrt___1 = factor(data$antiviral_cmtrt___1,levels=c("0","1"))
# data$antiviral_cmtrt___2 = factor(data$antiviral_cmtrt___2,levels=c("0","1"))
# data$antiviral_cmtrt___3 = factor(data$antiviral_cmtrt___3,levels=c("0","1"))
# data$antiviral_cmtrt___4 = factor(data$antiviral_cmtrt___4,levels=c("0","1"))
# data$antiviral_cmtrt___5 = factor(data$antiviral_cmtrt___5,levels=c("0","1"))
# data$antiviral_cmtrt___6 = factor(data$antiviral_cmtrt___6,levels=c("0","1"))
# data$antiviral_cmtrt___7 = factor(data$antiviral_cmtrt___7,levels=c("0","1"))
# data$antiviral_cmtrt___8 = factor(data$antiviral_cmtrt___8,levels=c("0","1"))
# data$antiviral_cmtrt___10 = factor(data$antiviral_cmtrt___10,levels=c("0","1"))
# data$antiviral_cmtrt___11 = factor(data$antiviral_cmtrt___11,levels=c("0","1"))
# data$antiviral_cmtrt___9 = factor(data$antiviral_cmtrt___9,levels=c("0","1"))
# data$antibiotic_cmyn = factor(data$antibiotic_cmyn,levels=c("1","2","3"))
# data$iv_ab = factor(data$iv_ab,levels=c("1","2","3"))
# data$type_iv_ab___0 = factor(data$type_iv_ab___0,levels=c("0","1"))
# data$type_iv_ab___1 = factor(data$type_iv_ab___1,levels=c("0","1"))
# data$type_iv_ab___2 = factor(data$type_iv_ab___2,levels=c("0","1"))
# data$type_iv_ab___3 = factor(data$type_iv_ab___3,levels=c("0","1"))
# data$type_iv_ab___4 = factor(data$type_iv_ab___4,levels=c("0","1"))
# data$type_iv_ab___5 = factor(data$type_iv_ab___5,levels=c("0","1"))
# data$type_iv_ab___6 = factor(data$type_iv_ab___6,levels=c("0","1"))
# data$type_iv_ab___9 = factor(data$type_iv_ab___9,levels=c("0","1"))
# data$type_iv_ab___8 = factor(data$type_iv_ab___8,levels=c("0","1"))
# data$type_iv_ab___7 = factor(data$type_iv_ab___7,levels=c("0","1"))
# data$o_ab = factor(data$o_ab,levels=c("1","0"))
# data$type_o_ab___1 = factor(data$type_o_ab___1,levels=c("0","1"))
# data$type_o_ab___2 = factor(data$type_o_ab___2,levels=c("0","1"))
# data$type_o_ab___3 = factor(data$type_o_ab___3,levels=c("0","1"))
# data$type_o_ab___4 = factor(data$type_o_ab___4,levels=c("0","1"))
# data$type_o_ab___5 = factor(data$type_o_ab___5,levels=c("0","1"))
# data$type_o_ab___6 = factor(data$type_o_ab___6,levels=c("0","1"))
# data$type_o_ab___7 = factor(data$type_o_ab___7,levels=c("0","1"))
# data$type_o_ab___8 = factor(data$type_o_ab___8,levels=c("0","1"))
# data$corticost_cmyn = factor(data$corticost_cmyn,levels=c("1","2","3"))
# data$corticost_cmroute = factor(data$corticost_cmroute,levels=c("1","2","3"))
# data$anti_inflammatory___1 = factor(data$anti_inflammatory___1,levels=c("0","1"))
# data$anti_inflammatory___2 = factor(data$anti_inflammatory___2,levels=c("0","1"))
# data$other_anti_inflammatory = factor(data$other_anti_inflammatory,levels=c("1","2","3"))
# data$iv_imglob = factor(data$iv_imglob,levels=c("1","2","3"))
# data$imod = factor(data$imod,levels=c("1","2","3"))
# data$sys_anticoag = factor(data$sys_anticoag,levels=c("1","2","3"))
# data$anti_mal = factor(data$anti_mal,levels=c("1","2","3"))
# data$antifung_cmyn = factor(data$antifung_cmyn,levels=c("1","2","3"))
# data$experimental = factor(data$experimental,levels=c("1","2","3"))
# data$other_sc2_treatments = factor(data$other_sc2_treatments,levels=c("1","2","3"))
# data$vasopressors = factor(data$vasopressors,levels=c("1","2","3"))
# data$vasopressors_type___1 = factor(data$vasopressors_type___1,levels=c("0","1"))
# data$vasopressors_type___2 = factor(data$vasopressors_type___2,levels=c("0","1"))
# data$vasopressors_type___3 = factor(data$vasopressors_type___3,levels=c("0","1"))
# data$vasopressors_type___4 = factor(data$vasopressors_type___4,levels=c("0","1"))
# data$vasopressors_type___5 = factor(data$vasopressors_type___5,levels=c("0","1"))
# data$vasopressors_type___6 = factor(data$vasopressors_type___6,levels=c("0","1"))
# data$ecmo = factor(data$ecmo,levels=c("1","2","3"))
# data$blood_trans = factor(data$blood_trans,levels=c("1","2","3"))
# data$medication_complete = factor(data$medication_complete,levels=c("0","1","2"))
# data$dsterm = factor(data$dsterm,levels=c("1","2","3","4","5","8","6","7"))
# data$excluded_reason = factor(data$excluded_reason,levels=c("1","2","3"))
# data$final_dx_1 = factor(data$final_dx_1,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
# data$related_1 = factor(data$related_1,levels=c("1","2"))
# data$final_dx_2 = factor(data$final_dx_2,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
# data$related_2 = factor(data$related_2,levels=c("1","2","3"))
# data$final_dx_3 = factor(data$final_dx_3,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
# data$final_dx_4 = factor(data$final_dx_4,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
# data$final_dx_5 = factor(data$final_dx_5,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
# data$final_dx_6 = factor(data$final_dx_6,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
# data$related_3 = factor(data$related_3,levels=c("1","2","3"))
# data$outcome_complete = factor(data$outcome_complete,levels=c("0","1","2"))
# data$spirometry_complete = factor(data$spirometry_complete,levels=c("0","1","2"))
# data$fever_ws = factor(data$fever_ws,levels=c("1","0"))
# data$lumbar_punc = factor(data$lumbar_punc,levels=c("1","0"))
# data$csf_bacteria = factor(data$csf_bacteria,levels=c("1","0"))
# data$csf_vhs = factor(data$csf_vhs,levels=c("1","0","2"))
# data$csf_enterovirus = factor(data$csf_enterovirus,levels=c("1","0","2"))
# data$csf_sarscov2 = factor(data$csf_sarscov2,levels=c("1","0","2"))
# data$urine_collection = factor(data$urine_collection,levels=c("1","2","3","4","5"))
# data$urine_dipstik = factor(data$urine_dipstik,levels=c("1","2","3","4","5"))
# data$urine_culture = factor(data$urine_culture,levels=c("1","0","2"))
# data$fever_without_source_study_complete = factor(data$fever_without_source_study_complete,levels=c("0","1","2"))
# data$qc_stage = factor(data$qc_stage,levels=c("0","1","2","3","4"))
# data$first_analysis = factor(data$first_analysis,levels=c("1","0"))
# data$quality_control_complete = factor(data$quality_control_complete,levels=c("0","1","2"))
# 
# levels(data$hospital)=c("Clínica Infantil Colsubsidio (CIC)","Hospital Universitario Fundación Santa Fé de Bogotá (HUFSFB)","Instituto Roosevelt (IR)","Ministerio de Salud de Colombia","Universidad de los Andes","Hospital de Nariño","San José Centro","San José Infantil","Hospital Militar","Clínica Colsanitas S.A. Sede Clínica Pediatrica","Clínica Colsanitas S.A. Sede Santa María del Lago","Clínica Colsanitas S.A. Sede Clínica Reina Sofía","Clínica Colsanitas S.A. Sede Clínica Universitaria 14, Colombia","Hospital Regional de la Orinoquia")
# levels(data$center_id_complete)=c("Incomplete","Unverified","Complete")
# levels(data$sex)=c("Male","Female","Not specified")
# levels(data$last_15)=c("Yes","No","Unknown")
# levels(data$demographics_complete)=c("Incomplete","Unverified","Complete")
# levels(data$symptoms_epi_travel)=c("Yes","No","Unknown")
# levels(data$symptoms_epi_physical)=c("Yes","No","Unknown")
# levels(data$symptoms_epi_healthfac)=c("Yes","No","Unknown")
# levels(data$symptoms_epi_animal)=c("Yes","No","Unknown")
# levels(data$symptoms_epi_comm)=c("Yes","No","Unknown")
# levels(data$contact___1)=c("Unchecked","Checked")
# levels(data$contact___2)=c("Unchecked","Checked")
# levels(data$contact___3)=c("Unchecked","Checked")
# levels(data$contact___4)=c("Unchecked","Checked")
# levels(data$inclusion_criteria_complete)=c("Incomplete","Unverified","Complete")
# levels(data$anamnesis_complete)=c("Incomplete","Unverified","Complete")
# levels(data$comorb)=c("Yes","No")
# levels(data$chroniccard_mhyn)=c("Yes","No","Unknown")
# levels(data$hypertension_mhyn)=c("Yes","No","Unknown")
# levels(data$chronicpul_mhyn)=c("Yes","No","Unknown")
# levels(data$asthma_mhyn)=c("Yes","No","Unknown")
# levels(data$tb_mhyn)=c("Yes","No","Unknown")
# levels(data$resp_inf_mhyn)=c("Yes","No","Unknown")
# levels(data$renal_mhyn)=c("Yes","No","Unknown")
# levels(data$modliver_mhyn)=c("Yes","No","Unknown")
# levels(data$mildliv_mhyn)=c("Yes","No","Unknown")
# levels(data$chronicneu_mhyn)=c("Yes","No","Unknown")
# levels(data$malignantneo_mhyn)=c("Yes","No","Unknown")
# levels(data$chronhaemo_mhyn)=c("Yes","No","Unknown")
# levels(data$aidshiv_mhyn)=c("Yes","No","Unknown")
# levels(data$obesity_mhyn)=c("Yes","No","Unknown")
# levels(data$diabetiscomp_mhyn)=c("Yes","No","Unknown")
# levels(data$diabetes_mhyn)=c("Yes","No","Unknown")
# levels(data$inflammatory_mhyr)=c("Yes","No","Unknown")
# levels(data$rheumatology_mhyr)=c("Yes","No","Unknown")
# levels(data$kawa_mhyn)=c("Yes","No","Unknown")
# levels(data$kawa_fam_mhyn)=c("Yes","No","Unknown")
# levels(data$dementia_mhyn)=c("Yes","No","Unknown")
# levels(data$malnutrition_mhyn)=c("Yes","No","Unknown")
# levels(data$other_mhyn)=c("Yes","No","Unknown")
# levels(data$smoking_mhyn)=c("Yes","Never Smoker","Former Smoker")
# levels(data$immunosupressors)=c("Yes","No")
# levels(data$comorbidities_complete)=c("Incomplete","Unverified","Complete")
# levels(data$influenza_full_regimen)=c("Yes","No")
# levels(data$apsc_vcageind)=c("Yes","No","Unknown")
# levels(data$vaccines_complete)=c("Incomplete","Unverified","Complete")
# levels(data$anthropometry_complete)=c("Incomplete","Unverified","Complete")
# levels(data$dehydr)=c("Severe","Some","None")
# levels(data$fever_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$cough_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$sorethroat_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$runnynose_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$wheeze_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$chestpain_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$myalgia_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$jointpain_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$fatigue_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$shortbreath_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$lowerchest_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$headache_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$confusion_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$seizures_cecoccur_v2)=c("Yes","No","Unknown")
# levels(data$abdopain_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$vomit_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$diarrhoea_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$conjunct_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$oral_inf)=c("Yes","No","Unknown")
# levels(data$pale_skin)=c("Yes","No","Unknown")
# levels(data$rash_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$skinulcers_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$peri_inf)=c("Yes","No","Unknown")
# levels(data$lymp_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$bleed_ceoccur_v2)=c("Yes","No","Unknown")
# levels(data$cold_hands)=c("Yes","No","Unknown")
# levels(data$cap_refill)=c("Yes","No","Unknown")
# levels(data$sw_joints)=c("Yes","No","Unknown")
# levels(data$st_neck)=c("Yes","No","Unknown")
# levels(data$hypo_flop)=c("Yes","No","Unknown")
# levels(data$paralysis)=c("Yes","No","Unknown")
# levels(data$shock)=c("Yes","No","Unknown")
# levels(data$sens_alt)=c("Yes","No","Unknown")
# levels(data$admission_signs_and_symptoms_complete)=c("Incomplete","Unverified","Complete")
# levels(data$blood_tests_complete)=c("Incomplete","Unverified","Complete")
# levels(data$pcr_cov2_1)=c("Positive","Negative","Pending","Unavailable")
# levels(data$pcr_cov2_2)=c("Positive","Negative","Pending","Unavailable")
# levels(data$pcr_cov2_3)=c("Positive","Negative","Pending","Unavailable")
# levels(data$pcr_cov2_4)=c("Positive","Negative","Pending","Unavailable")
# levels(data$rapid_ag_test_covid___1)=c("Unchecked","Checked")
# levels(data$rapid_ag_test_covid___2)=c("Unchecked","Checked")
# levels(data$rapid_ag_test_covid_1)=c("Positive","Negative")
# levels(data$rapid_ag_test_covid_2)=c("Positive","Negative")
# levels(data$virus_obtained_pcr_16)=c("Yes","No")
# levels(data$pcr_types_virus_sr___1)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___2)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___3)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___4)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___5)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___6)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___7)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___8)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___9)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___10)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___11)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___12)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___13)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___14)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___15)=c("Unchecked","Checked")
# levels(data$pcr_types_virus_sr___16)=c("Unchecked","Checked")
# levels(data$pcr_atipical_sr)=c("Yes","No")
# levels(data$pcr_mn_sr)=c("Positive","Negative","Pending","Unavailable")
# levels(data$pcr_cn_sr)=c("Positive","Negative","Pending","Unavailable")
# levels(data$pcr_hib_sr)=c("Positive","Negative","Pending","Unavailable")
# levels(data$pcr_leg_sr)=c("Positive","Negative","Pending","Unavailable")
# levels(data$pcr_bordetella_sr)=c("Positive","Negative","Pending","Unavailable")
# levels(data$anti_influenza)=c("Positive","Negative","Not performed")
# levels(data$anti_rsv)=c("Positive","Negative","Not performed")
# levels(data$res_samples)=c("Yes","No")
# levels(data$respiratory_secretion_microbiology_complete)=c("Incomplete","Unverified","Complete")
# levels(data$first_sr_sc2)=c("Yes","No","Sample collection pending","Results pending")
# levels(data$first_sr_sc2_type)=c("Rapid test","ELISA","Neutralization test","Other")
# levels(data$igm_sc2_1)=c("Positive","Negative","Pending","Unavailable")
# levels(data$igg_sc2_1)=c("Positive","Negative","Pending","Unavailable")
# levels(data$second_sr_sc2)=c("Yes","No","Sample collection pending","Results pending")
# levels(data$second_sr_sc2_type)=c("Rapid test","ELISA","Neutralization test","Other")
# levels(data$igm_sc2_2)=c("Positive","Negative","Pending","Unavailable")
# levels(data$igg_sc2_2)=c("Positive","Negative","Pending","Unavailable")
# levels(data$blood_culture)=c("Yes","No")
# levels(data$probable_bacterial_etiology_hemoculture)=c("S. pneumoniae","S. aureus","S. pyogenes","Other (specify)")
# levels(data$other_bacteria_hemoculture)=c("Yes","No")
# levels(data$first_sr_atipical)=c("Yes","No","Sample collection pending","Results pending")
# levels(data$serology1_igm_mn)=c("Positive","Negative","Pending","Unavailable")
# levels(data$serology1_igg_mn)=c("Positive","Negative","Pending","Unavailable")
# levels(data$serology1_igm_cn)=c("Positive","Negative","Pending","Unavailable")
# levels(data$serology1_igg_cn)=c("Positive","Negative","Pending","Unavailable")
# levels(data$second_sr_atipical)=c("Yes","No","Sample collection pending","Results pending")
# levels(data$serology2_igm_mn)=c("Positive","Negative","Pending","Unavailable")
# levels(data$serology2_igg_mn)=c("Positive","Negative","Pending","Unavailable")
# levels(data$serology2_igm_cn)=c("Positive","Negative","Pending","Unavailable")
# levels(data$serology2_igg_cn)=c("Positive","Negative","Pending","Unavailable")
# levels(data$seroconversion_mn)=c("Yes","No","Pending","Unavailable")
# levels(data$blood_samples)=c("Yes","No")
# levels(data$plasma_samples)=c("Yes","No")
# levels(data$blood_microbiology_complete)=c("Incomplete","Unverified","Complete")
# levels(data$codetection)=c("Yes","No","Pending","Unknown due to lack of microbiological data")
# levels(data$codetecion_type)=c("Virus-Virus","Virus-Bacteria")
# levels(data$codetecion_complete)=c("Incomplete","Unverified","Complete")
# levels(data$thoracentesis_done)=c("Yes","No")
# levels(data$ag_pneumo_pf)=c("Positive","Negative","Not performed")
# levels(data$pcr_pneumo_pf)=c("Positive","Negative","Not performed")
# levels(data$culture_pf)=c("Positive","Negative")
# levels(data$cultured_bacteria_pf)=c("Pneumococcus","S. pyogenes","S. aureus","Haemophilus influenzae","Other")
# levels(data$pleural_fluid_microbiology_complete)=c("Incomplete","Unverified","Complete")
# levels(data$oxygen_therapy)=c("Yes","No")
# levels(data$hft)=c("Yes","No")
# levels(data$cpap)=c("Yes","No")
# levels(data$picu_admission)=c("Yes","No")
# levels(data$mechanical_ventilation)=c("Yes","No")
# levels(data$nimv)=c("Yes","No")
# levels(data$imv)=c("Yes","No")
# levels(data$evolution_complete)=c("Incomplete","Unverified","Complete")
# levels(data$complications)=c("Yes","No")
# levels(data$pleural_effusion)=c("Yes","No")
# levels(data$effusion_type)=c("Not complicated","Complicated (pH< 7 and/or partitions)")
# levels(data$corticosteroids)=c("Yes","No")
# levels(data$pleural_drainage)=c("Yes","No")
# levels(data$drainage_type)=c("Pleural tube","VATS","Evacuating thoracentesis only")
# levels(data$pneumatocele_abscess)=c("Yes","No")
# levels(data$pneumothorax)=c("Yes","No")
# levels(data$cardio_comp)=c("Yes","No")
# levels(data$cardio_comp_myoc)=c("Yes","No")
# levels(data$cardio_comp_peri)=c("Yes","No")
# levels(data$cardio_comp_valve)=c("Yes","No")
# levels(data$cardio_comp_arry)=c("Yes","No")
# levels(data$cardio_comp_cor)=c("Yes","No")
# levels(data$cardio_comp_ane)=c("Yes","No")
# levels(data$sepsis)=c("Yes","No")
# levels(data$renal_failure)=c("Yes","No")
# levels(data$kawa)=c("Yes","No")
# levels(data$complications_complete)=c("Incomplete","Unverified","Complete")
# levels(data$xray_result_1)=c("Condensation","Other infiltrates","Normal")
# levels(data$x_ray_1_reported_by___1)=c("Unchecked","Checked")
# levels(data$x_ray_1_reported_by___2)=c("Unchecked","Checked")
# levels(data$x_ray_1_reported_by___3)=c("Unchecked","Checked")
# levels(data$x_ray_1_result_ext)=c("Condensation","Other infiltrates","Normal")
# levels(data$xray_result_2)=c("Condensation","Other infiltrates","Normal")
# levels(data$x_ray_2_reported_by___1)=c("Unchecked","Checked")
# levels(data$x_ray_2_reported_by___2)=c("Unchecked","Checked")
# levels(data$x_ray_2_reported_by___3)=c("Unchecked","Checked")
# levels(data$x_ray_2_result_ext)=c("Condensation","Other infiltrates","Normal")
# levels(data$xray_result_3)=c("Condensation","Other infiltrates","Normal")
# levels(data$x_ray_3_reported_by___1)=c("Unchecked","Checked")
# levels(data$x_ray_3_reported_by___2)=c("Unchecked","Checked")
# levels(data$x_ray_3_reported_by___3)=c("Unchecked","Checked")
# levels(data$x_ray_3_result_ext)=c("Condensation","Other infiltrates","Normal")
# levels(data$cardiac_img)=c("Yes","No","Unknown")
# levels(data$radiology_complete)=c("Incomplete","Unverified","Complete")
# levels(data$oro_fluids)=c("Yes","No","Unknown")
# levels(data$iv_fluids)=c("Yes","No","Unknown")
# levels(data$antiviral_cmyn)=c("Yes","No","Unknown")
# levels(data$antiviral_cmtrt___1)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___2)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___3)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___4)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___5)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___6)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___7)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___8)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___10)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___11)=c("Unchecked","Checked")
# levels(data$antiviral_cmtrt___9)=c("Unchecked","Checked")
# levels(data$antibiotic_cmyn)=c("Yes","No","Unknown")
# levels(data$iv_ab)=c("Yes","No","Data unavailable")
# levels(data$type_iv_ab___0)=c("Unchecked","Checked")
# levels(data$type_iv_ab___1)=c("Unchecked","Checked")
# levels(data$type_iv_ab___2)=c("Unchecked","Checked")
# levels(data$type_iv_ab___3)=c("Unchecked","Checked")
# levels(data$type_iv_ab___4)=c("Unchecked","Checked")
# levels(data$type_iv_ab___5)=c("Unchecked","Checked")
# levels(data$type_iv_ab___6)=c("Unchecked","Checked")
# levels(data$type_iv_ab___9)=c("Unchecked","Checked")
# levels(data$type_iv_ab___8)=c("Unchecked","Checked")
# levels(data$type_iv_ab___7)=c("Unchecked","Checked")
# levels(data$o_ab)=c("Yes","No")
# levels(data$type_o_ab___1)=c("Unchecked","Checked")
# levels(data$type_o_ab___2)=c("Unchecked","Checked")
# levels(data$type_o_ab___3)=c("Unchecked","Checked")
# levels(data$type_o_ab___4)=c("Unchecked","Checked")
# levels(data$type_o_ab___5)=c("Unchecked","Checked")
# levels(data$type_o_ab___6)=c("Unchecked","Checked")
# levels(data$type_o_ab___7)=c("Unchecked","Checked")
# levels(data$type_o_ab___8)=c("Unchecked","Checked")
# levels(data$corticost_cmyn)=c("Yes","No","Unknown")
# levels(data$corticost_cmroute)=c("Oral","Intravenous","Inhaled")
# levels(data$anti_inflammatory___1)=c("Unchecked","Checked")
# levels(data$anti_inflammatory___2)=c("Unchecked","Checked")
# levels(data$other_anti_inflammatory)=c("Yes","No","Unknown")
# levels(data$iv_imglob)=c("Yes","No","Unknown")
# levels(data$imod)=c("Yes","No","Unknown")
# levels(data$sys_anticoag)=c("Yes","No","Unknown")
# levels(data$anti_mal)=c("Yes","No","Unknown")
# levels(data$antifung_cmyn)=c("Yes","No","Unknown")
# levels(data$experimental)=c("Yes","No","Unknown")
# levels(data$other_sc2_treatments)=c("Yes","No","Unknown")
# levels(data$vasopressors)=c("Yes","No","Unknown")
# levels(data$vasopressors_type___1)=c("Unchecked","Checked")
# levels(data$vasopressors_type___2)=c("Unchecked","Checked")
# levels(data$vasopressors_type___3)=c("Unchecked","Checked")
# levels(data$vasopressors_type___4)=c("Unchecked","Checked")
# levels(data$vasopressors_type___5)=c("Unchecked","Checked")
# levels(data$vasopressors_type___6)=c("Unchecked","Checked")
# levels(data$ecmo)=c("Yes","No","Unknown")
# levels(data$blood_trans)=c("Yes","No","Unknown")
# levels(data$medication_complete)=c("Incomplete","Unverified","Complete")
# levels(data$dsterm)=c("Discharged alive (not hospitalized)","Discharged alive after hospitalization","Transfer to other facility","Death","Palliative discharge","Currently hospitalized","Unknown","Excluded")
# levels(data$excluded_reason)=c("Not fulfilled inclusion criteria","Withdrawal of consent","Other")
# levels(data$final_dx_1)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
# levels(data$related_1)=c("Related","Unclear")
# levels(data$final_dx_2)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
# levels(data$related_2)=c("Related","Not Related","Unclear")
# levels(data$final_dx_3)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
# levels(data$final_dx_4)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
# levels(data$final_dx_5)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
# levels(data$final_dx_6)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
# levels(data$related_3)=c("Related","Not Related","Unclear")
# levels(data$outcome_complete)=c("Incomplete","Unverified","Complete")
# levels(data$spirometry_complete)=c("Incomplete","Unverified","Complete")
# levels(data$fever_ws)=c("Yes","No")
# levels(data$lumbar_punc)=c("Yes","No")
# levels(data$csf_bacteria)=c("Positive","Negative")
# levels(data$csf_vhs)=c("Positive","Negative","Not performed")
# levels(data$csf_enterovirus)=c("Positive","Negative","Not performed")
# levels(data$csf_sarscov2)=c("Positive","Negative","Not performed")
# levels(data$urine_collection)=c("Catheter","Tapping / spontaneus","Perineal bag","Puncture","Urine collection not performed")
# levels(data$urine_dipstik)=c("Leucocytes","Nitrites","Leucocytes + Nitrites","Normal","Not performed")
# levels(data$urine_culture)=c("Positive","Negative","Not performed")
# levels(data$fever_without_source_study_complete)=c("Incomplete","Unverified","Complete")
# levels(data$qc_stage)=c("Not started","Clinical quality control performed, waiting for answers to clinical queries","Clinical queries resolved, pending data quality control","Data quality control performed, waiting for answers to data queries","Quality control completed")
# levels(data$first_analysis)=c("Yes","No")
# levels(data$quality_control_complete)=c("Incomplete","Unverified","Complete")
# 
# #Arreglar formato de variables fecha: 
# 
# #fechas <- data %>% select(contains("date"))
# data$admission_date %<>% ymd()
# data$patient_birth_date %<>% ymd()
# data$fever_start_date %<>%ymd()
# data$pcr_cov2_1_date %<>% ymd()
# data$pcr_cov2_2_date %<>% ymd()
# data$pcr_cov2_3_date %<>% ymd()
# data$pcr_cov2_4_date %<>% ymd()
# data$first_sr_sc2_date %<>% ymd()
# data$second_sr_sc2_date %<>% ymd()
# data$date_ser_1 %<>% ymd()
# data$date_ser_2 %<>% ymd()
# data$fever_end_date %<>% ymd()
# data$oxigen_start_date %<>% ymd()
# data$oxigen_end_date %<>% ymd()
# data$hft_start_date %<>% ymd()
# data$hft_end_date %<>% ymd()
# data$cpap_start_date %<>% ymd()
# data$cpap_end_date %<>% ymd()
# data$picu_admission_date %<>% ymd()
# data$picu_discharge_date %<>% ymd()
# data$nimv_start_date %<>% ymd()
# data$nimv_end_date %<>% ymd()
# data$imv_start_date %<>% ymd()
# data$imv_end_date %<>% ymd()
# data$discharge_date %<>% ymd()
# data$x_ray_1_date %<>% ymd()
# data$x_ray_2_date %<>% ymd()
# data$x_ray_3_date %<>% ymd()
# data$lung_ct_date %<>% ymd()
# data$iv_ab_start_date %<>% ymd()
# data$iv_ab_end_date %<>% ymd()
# data$o_ab_start_date %<>% ymd()
# data$o_ab_end_date %<>% ymd()
# data$qc_date %<>% ymd()
# 
# #Numericas: 
# data$age_months%<>%as.numeric()

```


```{r}
# #Setting Labels

label(data$record)="Identification"
label(data$hospital)="Hospital"
label(data$health_worker_name)="Who fills the paper data notebook (name)"
label(data$center_id_complete)="Complete?"
label(data$patient_birth_date)="Patients date of birth"
label(data$admission_date)="Date of admission"
label(data$age_months)="Age in months"
label(data$sex)="Sex at Birth:"
label(data$last_15)="Has the child been previously admitted to hospital in the last 15 days?"
label(data$demographics_complete)="Complete?"
label(data$symptoms_epi_travel)="A history of travel to an area with documented cases of novel coronavirus infection"
label(data$symptoms_epi_physical)="Close contact with a confirmed or probable case of nCoV infection"
label(data$symptoms_epi_healthfac)="Presence in a healthcare facility where nCoV infections have been managed"
label(data$symptoms_epi_animal)="Direct contact with animals in countries where the nCoV is known to be circulating in animal populations or where human infections have occurred as a result of presumed zoonotic transmission"
label(data$symptoms_epi_comm)="Area with community transmission"
label(data$contact___1)="Close contact (choice=Health care associated exposure, including providing direct care for novel coronavirus patients, e.g. health care worker, working with health care workers infected with novel coronavirus, visiting patients or staying in the same close environment of a novel coronavirus patient, or direct exposure to body fluids or specimens including aerosols)"
label(data$contact___2)="Close contact (choice=Working together in close proximity or sharing the same classroom environment with a novel coronavirus patient)"
label(data$contact___3)="Close contact (choice=Traveling together with novel coronavirus patient in any kind of conveyance)"
label(data$contact___4)="Close contact (choice=Living in the same household as a novel coronavirus patient)"
label(data$index_case)="Who is the index case (father, mother, uncle ...)"
label(data$inclusion_criteria_complete)="Complete?"
label(data$fever_start_date)="Fever onset date"
label(data$fever_days)="Fever days (from start to admission, including start day)"
label(data$fever_days_total)="Fever days (from start to end, including start day)"
label(data$fever_3)="Fever days >= 3"
label(data$anamnesis_complete)="Complete?"
label(data$comorb)="Comorbidities"
label(data$chroniccard_mhyn)="Chronic cardiac disease, including congenital heart disease (not hypertesnion)"
label(data$hypertension_mhyn)="Hypertension"
label(data$chronicpul_mhyn)="Chronic pulmonary disease (not asthma)"
label(data$asthma_mhyn)="Asthma (or recurrent wheezing)"
label(data$tb_mhyn)="Tuberculosis"
label(data$resp_inf_mhyn)="History of respiratory infection in the previous 4 weeks prior to current illness?"
label(data$renal_mhyn)="Chronic kidney disease"
label(data$modliver_mhyn)="Moderate or severe liver disease"
label(data$mildliv_mhyn)="Mild Liver disease"
label(data$chronicneu_mhyn)="Chronic neurological disorder"
label(data$malignantneo_mhyn)="Malignant neoplasm"
label(data$chronhaemo_mhyn)="Chronic hematologic disease"
label(data$aidshiv_mhyn)="AIDS/HIV"
label(data$obesity_mhyn)="Obesity (as defined by clinical staff)"
label(data$diabetiscomp_mhyn)="Diabetes with complications"
label(data$diabetes_mhyn)="Diabetes without complications"
label(data$inflammatory_mhyr)="Inflammatory disorder"
label(data$rheumatology_mhyr)="Rheumatologic disorder"
label(data$kawa_mhyn)="Past history of Kawasaki disease"
label(data$kawa_fam_mhyn)="Family history of Kawasaki disease"
label(data$dementia_mhyn)="Dementia"
label(data$malnutrition_mhyn)="Malnutrition"
label(data$other_mhyn)="Other relevant risk factors"
label(data$inf_reum_type)="Please specify inflammatory or rheumatological disorder"
label(data$smoking_mhyn)="Smoking"
label(data$otherrisktext)="Other  relevant risk factor; Specify"
label(data$immunosupressors)="On immunosuppressive medication?"
label(data$comorbidities_complete)="Complete?"
label(data$influenza_full_regimen)="Influenza vaccine (current year)"
label(data$apsc_vcageind)="Vaccinations appropriate for age/country?"
label(data$vaccines_complete)="Complete?"
label(data$weight)="Weight (grams)"
label(data$weight_percentile)="Weight percentile"
label(data$size)="Size (cm)"
label(data$size_percentile)="Size percentile"
label(data$anthropometry_complete)="Complete?"
label(data$temp_vsorres)="Temperature"
label(data$hr_vsorres)="Heart Rate"
label(data$rr_vsorres)="Respiratory Rate"
label(data$sysbp_vsorres)="Systolic blood pressure"
label(data$admission_diabp_vsorres)="Diastolic blood pressure"
label(data$oxy_vsorres)="Oxygen saturation"
label(data$muac)="Mid-upper arm circumference"
label(data$dehydr)="Dehydratation"
label(data$fever_ceoccur_v2)="History of fever"
label(data$cough_ceoccur_v2)="Cough"
label(data$sorethroat_ceoccur_v2)="Sore throat"
label(data$runnynose_ceoccur_v2)="Runny nose (Rhinorrhoea)"
label(data$wheeze_ceoccur_v2)="Wheezing"
label(data$chestpain_ceoccur_v2)="Chest pain"
label(data$myalgia_ceoccur_v2)="Muscle aches (Myalgia)"
label(data$jointpain_ceoccur_v2)="Joint pain (Arthralgia)"
label(data$fatigue_ceoccur_v2)="Fatigue / Malaise"
label(data$shortbreath_ceoccur_v2)="Shortness of breath or work of breathing (Dyspnea)"
label(data$lowerchest_ceoccur_v2)="Lower chest wall indrawing"
label(data$headache_ceoccur_v2)="Headache"
label(data$confusion_ceoccur_v2)="Altered consciousness / confusion"
label(data$seizures_cecoccur_v2)="Seizures"
label(data$abdopain_ceoccur_v2)="Abdominal pain"
label(data$vomit_ceoccur_v2)="Vomiting / Nausea"
label(data$diarrhoea_ceoccur_v2)="Diarrhoea"
label(data$conjunct_ceoccur_v2)="Conjunctivitis"
label(data$oral_inf)="Oral mucosal inflammation signs"
label(data$pale_skin)="Pale/mottled skin"
label(data$rash_ceoccur_v2)="Skin rash"
label(data$skinulcers_ceoccur_v2)="Skin ulcers"
label(data$peri_inf)="Peripheral cutaneous inflammation signs (hands or feet)"
label(data$lymp_ceoccur_v2)="Lymphadenopathy"
label(data$bleed_ceoccur_v2)="Bleeding (Haemorrhage)"
label(data$cold_hands)="Cold hands/feet"
label(data$cap_refill)="Capillary refill time > 2 seconds ?"
label(data$sw_joints)="Swollen joints"
label(data$st_neck)="Stiff neck"
label(data$hypo_flop)="Hypotonia / floppiness"
label(data$paralysis)="Paralysis"
label(data$shock)="Shock signs"
label(data$sens_alt)="Alteration in taste or smell"
label(data$admission_signs_and_symptoms_complete)="Complete?"
label(data$hb)="Hemoglobin"
label(data$leukocytes)="Leukocytes"
label(data$neutrophils)="Neutrophils"
label(data$lymphocytes)="Lymphocytes"
label(data$platelets)="Platelets"
label(data$aptt_aptr)="Activated Partial Thromboplastin Time / Ratio (APTT / APTR)"
label(data$pt)="Prothrombin Time (PT)"
label(data$inr)="International Normalized Ratio (INR)"
label(data$fibrino)="Fibrinogen"
label(data$c_reactive_protein)="C-reactive protein"
label(data$procalcitonin)="Procalcitonin"
label(data$cpk)="CPK"
label(data$alt_gpt)="Alanine aminotransferase-GPT"
label(data$ast_got)="Aspartate aminotransferase-GOT"
label(data$urea)="Urea"
label(data$creatinin)="Creatinine"
label(data$ldh)="Lactate dehydrogenase"
label(data$albumin)="Albumin"
label(data$sodium)="Serum sodium"
label(data$d_dimer)="Dimer-D"
label(data$il_6)="IL-6"
label(data$ferritin)="Ferritin"
label(data$trig)="Triglycerides"
label(data$bilirubin)="Total bilirubin"
label(data$lactate)="Lactate"
label(data$ph)="pH"
label(data$po2)="pO2"
label(data$pco2)="pCO2"
label(data$blood_tests_complete)="Complete?"
label(data$pcr_cov2_1)="SARS-CoV-2 PCR at diagnosis"
label(data$ct_cov2_1)="Cycle threshold (Ct) of SARS-CoV-2 PCR at diagnosis"
label(data$pcr_cov2_1_date)="Date of SARS-CoV-2 PCR at diagnosis"
label(data$pcr_cov2_2)="SARS-CoV-2 PCR at visit 2"
label(data$ct_cov2_2)="Cycle threshold (Ct) of SARS-CoV-2 PCR at visit 2"
label(data$pcr_cov2_2_date)="Date of SARS-CoV-2 PCR at visit 2"
label(data$pcr_cov2_3)="SARS-CoV-2 PCR at visit 3"
label(data$ct_cov2_3)="Cycle threshold (Ct) of SARS-CoV-2 PCR at visit 3"
label(data$pcr_cov2_3_date)="Date of SARS-CoV-2 PCR at visit 3"
label(data$pcr_cov2_4)="SARS-CoV-2 PCR at visit 4"
label(data$ct_cov2_4)="Cycle threshold (Ct) of SARS-CoV-2 PCR at visit 4"
label(data$pcr_cov2_4_date)="Date of SARS-CoV-2 PCR at visit 4"
label(data$rapid_ag_test_covid___1)="Rapid Antigenic Test (choice=Nasopharyngeal smear)"
label(data$rapid_ag_test_covid___2)="Rapid Antigenic Test (choice=Saliva)"
label(data$rapid_ag_test_covid_1)="Nasopharyngeal smear result"
label(data$rapid_ag_test_covid_2)="Saliva result"
label(data$virus_obtained_pcr_16)="PCR obtained for 16 viruses in respiratory secretion"
label(data$pcr_types_virus_sr___1)="Positive result in respiratory secretion PCR (choice=VRS)"
label(data$pcr_types_virus_sr___2)="Positive result in respiratory secretion PCR (choice=hMPV)"
label(data$pcr_types_virus_sr___3)="Positive result in respiratory secretion PCR (choice=PIV 1)"
label(data$pcr_types_virus_sr___4)="Positive result in respiratory secretion PCR (choice=PIV 2)"
label(data$pcr_types_virus_sr___5)="Positive result in respiratory secretion PCR (choice=PIV 3)"
label(data$pcr_types_virus_sr___6)="Positive result in respiratory secretion PCR (choice=PIV 4)"
label(data$pcr_types_virus_sr___7)="Positive result in respiratory secretion PCR (choice=Influenza A)"
label(data$pcr_types_virus_sr___8)="Positive result in respiratory secretion PCR (choice=Influenza B)"
label(data$pcr_types_virus_sr___9)="Positive result in respiratory secretion PCR (choice=hBoV)"
label(data$pcr_types_virus_sr___10)="Positive result in respiratory secretion PCR (choice=ADV)"
label(data$pcr_types_virus_sr___11)="Positive result in respiratory secretion PCR (choice=EV-hRV)"
label(data$pcr_types_virus_sr___12)="Positive result in respiratory secretion PCR (choice=Rhinovirus)"
label(data$pcr_types_virus_sr___13)="Positive result in respiratory secretion PCR (choice=CoV 229E)"
label(data$pcr_types_virus_sr___14)="Positive result in respiratory secretion PCR (choice=CoV OC43)"
label(data$pcr_types_virus_sr___15)="Positive result in respiratory secretion PCR (choice=CoV NL63)"
label(data$pcr_types_virus_sr___16)="Positive result in respiratory secretion PCR (choice=CoV HKU12)"
label(data$pcr_atipical_sr)="Obtained PCR sample for atypical respiratory secretion?"
label(data$pcr_mn_sr)="PCR Mycoplasma pneumoniae in respiratory secretion"
label(data$pcr_cn_sr)="PCR Chlamydophila pneumoniae in respiratory secretion"
label(data$pcr_hib_sr)="Haemophilus influenzae PCR in respiratory secretion"
label(data$pcr_leg_sr)="PCR Legionella in respiratory secretion"
label(data$pcr_bordetella_sr)="PCR Bordetella in respiratory secretion"
label(data$anti_influenza)="Antigen Influenza"
label(data$anti_rsv)="Antigen RSV"
label(data$res_samples)="Respiratory samples stored?"
label(data$respiratory_secretion_microbiology_complete)="Complete?"
label(data$first_sr_sc2)="Acute phase serology SARS-CoV-2 performed"
label(data$first_sr_sc2_type)="Acute phase serology test"
label(data$first_sr_sc2_type_ot)="Please, specify other test"
label(data$first_sr_sc2_date)="Date of acute phase serology SARS-CoV-2"
label(data$igm_sc2_1)="Acute phase serology IgM SARS-CoV-2"
label(data$igg_sc2_1)="Acute phase serology IgG SARS-CoV-2"
label(data$second_sr_sc2)="Follow-up serology SARS-CoV-2 performed"
label(data$second_sr_sc2_type)="Follow-up serology test"
label(data$second_sr_sc2_type_ot)="Please, specify other test"
label(data$second_sr_sc2_date)="Date of follow-up serology SARS-CoV-2"
label(data$igm_sc2_2)="Follow-up serology IgM SARS-CoV-2"
label(data$igg_sc2_2)="Follow-up serology IgG SARS-CoV-2"
label(data$sr_sc2_days)="Days from acute phase and follow-up serology for SARS-COV-2 (including the day when acute phase serology was done)"
label(data$blood_culture)="Blood culture for significant bacteria"
label(data$probable_bacterial_etiology_hemoculture)="Most likely bacterial aetiology in blood culture"
label(data$probable_text)="Please, specify"
label(data$other_bacteria_hemoculture)="Other bacteria in blood culture"
label(data$probable_text_2)="Please, specify"
label(data$first_sr_atipical)="First atypical serology performed"
label(data$date_ser_1)="Date of first atypical bacteria serology"
label(data$serology1_igm_mn)="Serology 1 IgM Mycoplasma pneumoniae"
label(data$serology1_igg_mn)="Serology 1 IgG Mycoplasma pneumoniae"
label(data$title1_igg_mn)="Title 1 IgG Mycoplasma pneumoniae"
label(data$serology1_igm_cn)="Serology 1 IgM Chlamydophila pneumoniae"
label(data$serology1_igg_cn)="Serology 1 IgG Chlamydophila pneumoniae"
label(data$title1_igg_cn)="Title 1 IgG Chlamydophila pneumoniae"
label(data$second_sr_atipical)="Second atypical serology performed"
label(data$date_ser_2)="Date of second atypical bacteria serology"
label(data$serology2_igm_mn)="Serology 2 IgM Mycoplasma pneumoniae"
label(data$serology2_igg_mn)="Serology 2 IgG Mycoplasma pneumoniae"
label(data$title2_igg_mn)="Title 2 IgG Mycoplasma pneumoniae"
label(data$serology2_igm_cn)="Serology 2 IgM Chlamydophila pneumoniae"
label(data$serology2_igg_cn)="Serology 2 IgG Chlamydophila pneumoniae"
label(data$title_igg_mn)="Title 2 IgG Chlamydophila pneumoniae"
label(data$seroconversion_mn)="Seroconversion"
label(data$blood_samples)="Whole blood samples stored?"
label(data$plasma_samples)="Plasma samples stored?"
label(data$blood_microbiology_complete)="Complete?"
label(data$codetection)="Codetection"
label(data$codetecion_type)="Codetection type"
label(data$codetecion_complete)="Complete?"
label(data$thoracentesis_done)="Thoracentesis performed"
label(data$ph_thoracentesis)="pH thoracentesis"
label(data$ag_pneumo_pf)="Pneumococcal antigen in pleural fluid"
label(data$pcr_pneumo_pf)="Pleural fluid pneumococcal PCR"
label(data$culture_pf)="Pleural fluid culture"
label(data$cultured_bacteria_pf)="Bacteria grown in pleural fluid"
label(data$other_cultured_bacteria_pf)="Other bacteria in pleural fluid culture"
label(data$pleural_fluid_microbiology_complete)="Complete?"
label(data$fever_end_date)="End date of fever"
label(data$oxygen_therapy)="Oxygen therapy"
label(data$oxigen_start_date)="Oxygen therapy start date"
label(data$oxigen_end_date)="End date oxygen therapy"
label(data$oxygen_therapy_time)="Days of oxygen therapy (including start day)"
label(data$hft)="High flow therapy"
label(data$hft_start_date)="High flow start date"
label(data$hft_end_date)="High flow end date"
label(data$hft_time)="Days of high flow therapy (including start day)"
label(data$cpap)="CPAP"
label(data$cpap_start_date)="CPAP start date"
label(data$cpap_end_date)="CPAP end date"
label(data$cpap_time)="Days of CPAP (including start day)"
label(data$picu_admission)="Admission to PICU"
label(data$picu_admission_date)="PICU admission date"
label(data$picu_discharge_date)="PICU discharge date"
label(data$picu_time)="Days of PICU admission (including admission day)"
label(data$mechanical_ventilation)="Mechanical ventilation"
label(data$nimv)="Noninvasive mechanical ventilation"
label(data$nimv_start_date)="Noninvasive mechanical ventilation start date"
label(data$nimv_end_date)="Noninvasive mechanical ventilation end date"
label(data$nimv_time)="Days of noninvasive mechanical ventilation (including start day)"
label(data$imv)="Invasive mechanical ventilation"
label(data$imv_start_date)="Invasive mechanical ventilation start date"
label(data$imv_end_date)="Invasive mechanical ventilation end date"
label(data$imv_time)="Days of invasive mechanical ventilation (including start day)"
label(data$discharge_date)="Hospital discharge date"
label(data$hosp_time)="Days of admission (including admission day)"
label(data$evolution_complete)="Complete?"
label(data$complications)="Complications (including new-onset signs or diagnosis after admission, such as Kawasaki-like / Inflammatory Syndrome symptoms)"
label(data$pleural_effusion)="Pleural effusion"
label(data$effusion_type)="Type of pleural effusion"
label(data$corticosteroids)="Systemic corticosteroids"
label(data$pleural_drainage)="Pleural drainage"
label(data$drainage_type)="Drain type"
label(data$pneumatocele_abscess)="Necrotizing pneumonia / abscess / pneumatocele"
label(data$pneumothorax)="Pneumothorax"
label(data$cardio_comp)="Cardiological complications"
label(data$cardio_comp_myoc)="Myocarditis / myocardial dysfunction"
label(data$cardio_comp_peri)="Pericarditis"
label(data$cardio_comp_valve)="Valve dysfunction"
label(data$cardio_comp_arry)="Arrhythmia"
label(data$cardio_comp_cor)="Coronary abnormalities"
label(data$cardio_comp_ane)="Aneurysms"
label(data$cardio_comp_bnp)="NT-proBNP"
label(data$cardio_comp_trop)="Troponin I"
label(data$cardio_comp_other)="Other cardiologic complications"
label(data$sepsis)="Sepsis"
label(data$renal_failure)="Renal failure"
label(data$kawa)="Kawasaki-like / Inflammatory Syndrome symptoms"
label(data$other_complications)="Other complications"
label(data$complications_complete)="Complete?"
label(data$x_ray_1)="X-ray 1 image"
label(data$x_ray_1_date)="Date of X-ray 1"
label(data$xray_result_1)="Interpretation of first radiological image"
label(data$x_ray_1_reported_by___1)="Responsible for first radiological image interpretation (choice=Clinician)"
label(data$x_ray_1_reported_by___2)="Responsible for first radiological image interpretation (choice=Radiology report)"
label(data$x_ray_1_reported_by___3)="Responsible for first radiological image interpretation (choice=Researcher)"
label(data$x_ray_1_result_ext)="First radiological image read by external researcher not involved with the patient"
label(data$x_ray_2)="X-ray 2 image"
label(data$x_ray_2_date)="Date of X-ray 2"
label(data$xray_result_2)="Interpretation of second radiological image"
label(data$x_ray_2_reported_by___1)="Responsible for second radiological image interpretation (choice=Clinician)"
label(data$x_ray_2_reported_by___2)="Responsible for second radiological image interpretation (choice=Radiology report)"
label(data$x_ray_2_reported_by___3)="Responsible for second radiological image interpretation (choice=Researcher)"
label(data$x_ray_2_result_ext)="Second radiological image read by external researcher not involved with the patient"
label(data$x_ray_3)="X-ray 3 image"
label(data$x_ray_3_date)="Date of X-ray 3"
label(data$xray_result_3)="Interpretation of third radiological image"
label(data$x_ray_3_reported_by___1)="Responsible for third radiological image interpretation (choice=Clinician)"
label(data$x_ray_3_reported_by___2)="Responsible for third radiological image interpretation (choice=Radiology report)"
label(data$x_ray_3_reported_by___3)="Responsible for third radiological image interpretation (choice=Researcher)"
label(data$x_ray_3_result_ext)="Third radiological image read by external researcher not involved with the patient"
label(data$lung_ct)="Lung CT scan image"
label(data$lung_ct_date)="Date of Lung CT scan image"
label(data$cardiac_img)="Cardiac imaging performed?"
label(data$card_img_results)="Please, specify name of technique and findings"
label(data$radiology_complete)="Complete?"
label(data$oro_fluids)="Oral/orogastric fluids?"
label(data$iv_fluids)="Intravenous fluids?"
label(data$antiviral_cmyn)="Antiviral agent"
label(data$antiviral_cmtrt___1)="Specify antiviral agent (choice=Ribavirin)"
label(data$antiviral_cmtrt___2)="Specify antiviral agent (choice=Lopinavir/Ritonavir)"
label(data$antiviral_cmtrt___3)="Specify antiviral agent (choice=Interferon-alpha)"
label(data$antiviral_cmtrt___4)="Specify antiviral agent (choice=Interferon-beta)"
label(data$antiviral_cmtrt___5)="Specify antiviral agent (choice=Neuraminidase inhibitors)"
label(data$antiviral_cmtrt___6)="Specify antiviral agent (choice=Remdesivir)"
label(data$antiviral_cmtrt___7)="Specify antiviral agent (choice=Chloroquine)"
label(data$antiviral_cmtrt___8)="Specify antiviral agent (choice=Hydroxychloroquine)"
label(data$antiviral_cmtrt___10)="Specify antiviral agent (choice=Anakinra)"
label(data$antiviral_cmtrt___11)="Specify antiviral agent (choice=Ivermectin)"
label(data$antiviral_cmtrt___9)="Specify antiviral agent (choice=Other)"
label(data$antiviral_cmtype)="Specify other antiviral type"
label(data$antiviral_days)="Days with antiviral"
label(data$antibiotic_cmyn)="Antibiotic"
label(data$iv_ab)="Intravenous antibiotic"
label(data$type_iv_ab___0)="Type of intravenous antibiotic (choice=Ampicillin)"
label(data$type_iv_ab___1)="Type of intravenous antibiotic (choice=Cefotaxime)"
label(data$type_iv_ab___2)="Type of intravenous antibiotic (choice=Cefuroxime)"
label(data$type_iv_ab___3)="Type of intravenous antibiotic (choice=Vancomycin)"
label(data$type_iv_ab___4)="Type of intravenous antibiotic (choice=Meropenem)"
label(data$type_iv_ab___5)="Type of intravenous antibiotic (choice=Clindamycin)"
label(data$type_iv_ab___6)="Type of intravenous antibiotic (choice=Cefazolin)"
label(data$type_iv_ab___9)="Type of intravenous antibiotic (choice=Ceftriaxone)"
label(data$type_iv_ab___8)="Type of intravenous antibiotic (choice=Clavulanic acid)"
label(data$type_iv_ab___7)="Type of intravenous antibiotic (choice=Other (specify))"
label(data$other_iv_ab)="Other intravenous antibiotic"
label(data$iv_ab_start_date)="Intravenous antibiotic start date"
label(data$iv_ab_end_date)="Intravenous antibiotic end date"
label(data$iv_ab_days)="Days of intravenous antibiotic (including start date)"
label(data$o_ab)="Intrahospital oral antibiotic "
label(data$type_o_ab___1)="Oral antibiotic type (choice=Amoxicillin)"
label(data$type_o_ab___2)="Oral antibiotic type (choice=Amoxicillin-Clavulanic)"
label(data$type_o_ab___3)="Oral antibiotic type (choice=Cefuroxime)"
label(data$type_o_ab___4)="Oral antibiotic type (choice=Azithromycin)"
label(data$type_o_ab___5)="Oral antibiotic type (choice=Erythromycin)"
label(data$type_o_ab___6)="Oral antibiotic type (choice=Clindamycin)"
label(data$type_o_ab___7)="Oral antibiotic type (choice=Cefadroxil)"
label(data$type_o_ab___8)="Oral antibiotic type (choice=Other (specify))"
label(data$other_o_ab)="Other oral antibiotic"
label(data$o_ab_start_date)="Oral antibiotic start date"
label(data$o_ab_end_date)="Oral antibiotic end date"
label(data$o_ab_days)="Days of oral antibiotic (including start date)"
label(data$azithromycin_or_erythromycin)="Oral Azithromycin or Erythromycin"
label(data$azithromycin_or_erythromycin_2d)="Oral Azithromycin or Erythromycin (during the first 2 days, 36h)"
label(data$corticost_cmyn)="Corticosteroids"
label(data$corticost_cmtrt)="Specify corticosteroid type"
label(data$corticost_cmdose)="Specify corticosteroid dose"
label(data$corticost_cmroute)="Specify corticosteroid route"
label(data$anti_inflammatory___1)="Anti-inflammatory treatment (choice=Ibuprofen)"
label(data$anti_inflammatory___2)="Anti-inflammatory treatment (choice=Tocilizumab)"
label(data$other_anti_inflammatory)="Other non-Steroidal Anti-Inflammatory Drugs (NSAIDs)"
label(data$other_anti_inflammatory_type)="Please, specify name of other NSAIDs"
label(data$iv_imglob)="Intravenous immune globulin"
label(data$iv_imglob_dose)="Daily intravenous immune globulin dose"
label(data$iv_imglob_days)="Days of intravenous immune globulin treatment"
label(data$imod)="Immunomodulators"
label(data$imod_type)="Please, specify name of immunomodulator"
label(data$sys_anticoag)="Systemic anticoagulation"
label(data$sys_anticoag_type)="Please, specify name of systemic anticoagulation agent"
label(data$anti_mal)="Antimalarial agent"
label(data$anti_mal_type)="Please, specify name of antimalarial agent"
label(data$antifung_cmyn)="Antifungal agent"
label(data$antifung_type)="Please, specify name of antifungal agent"
label(data$experimental)="Experimental agent"
label(data$experimental_type)="Please, specify name of experimental agent"
label(data$other_sc2_treatments)="Other medicationsÂ directed to cure COVID-19"
label(data$other_sc2_treatments_text)="Please, specify other COVID-19 treatments"
label(data$vasopressors)="Inotropes/vasopressors"
label(data$vasopressors_type___1)="Please, specify name of inotropes/vasopressors (choice=Adrenalin)"
label(data$vasopressors_type___2)="Please, specify name of inotropes/vasopressors (choice=Noradrenaline)"
label(data$vasopressors_type___3)="Please, specify name of inotropes/vasopressors (choice=Dopamine)"
label(data$vasopressors_type___4)="Please, specify name of inotropes/vasopressors (choice=Dobutamine)"
label(data$vasopressors_type___5)="Please, specify name of inotropes/vasopressors (choice=Milrinone)"
label(data$vasopressors_type___6)="Please, specify name of inotropes/vasopressors (choice=Other (please, specify in comments))"
label(data$ecmo)="Extracorporeal (ECMO) support"
label(data$blood_trans)="Blood transfusion"
label(data$medication_complete)="Complete?"
label(data$dsterm)="Patient outcome"
label(data$dsterm_other_text)="Please, specify which facility has been transferred to"
label(data$excluded_reason)="Reason for exclusion"
label(data$excluded_reason_ot)="Please specify reason for exclusion"
label(data$final_dx_global_concept)="Final diagnosis, ICD-10-CM concept/s"
label(data$final_dx_global_code)="Final diagnosis, ICD-10-CM code/s"
label(data$final_dx_1)="Primary diagnosis related with COVID-19"
label(data$related_1)="Is the primary diagnosis related to COVID-19?"
label(data$final_dx_2)="Secondary diagnosis: comorbidity which conditioned this admission"
label(data$related_2)="Is the secondary diagnosis related to COVID-19?"
label(data$final_dx_3)="Other diagnosis"
label(data$final_dx_4)="Other diagnosis"
label(data$final_dx_5)="Other diagnosis"
label(data$final_dx_6)="Other diagnosis"
label(data$related_3)="Is the other diagnosis related to COVID-19?"
label(data$outcome_complete)="Complete?"
label(data$fvc_6m)="Forced vital capacity (FVC)"
label(data$fev1_6m)="Forced expiratory volume (FEV1)"
label(data$esp_ave_flux_6m)="Average expiratory flow"
label(data$spirometry_complete)="Complete?"
label(data$fever_ws)="Fever without source at emergency ward admission"
label(data$lumbar_punc)="Lumbar puncture performed"
label(data$csf_bacteria)="CSF bacterial culture"
label(data$csf_baceria_type)="Bacteria isolated in CSF"
label(data$csf_vhs)="CSF VHS PCR "
label(data$csf_enterovirus)="CSF Enterovirus PCR "
label(data$csf_sarscov2)="CSF SARSCoV2 PCR "
label(data$csf_leuco)="Leucocytes in CSF"
label(data$csf_neutro)="Percentage of Neutrophils CSF"
label(data$csf_lympho)="Percentage of Lymphocytes in CSF"
label(data$protein_csf)="Protein in CSF"
label(data$glucose_csf)="Glucose in CSF"
label(data$urine_collection)="Urine collection method"
label(data$urine_dipstik)="Urine dipstick"
label(data$urine_culture)="Urine culture"
label(data$bacteria_urine)="Bacteria isolated in urine "
label(data$final_diagnosis)="Final diagnosis after fever without source episode, ICD-10-CM concept"
label(data$final_diagnosis_icd10)="Final diagnosis after fever without source episode, ICD-10-CM code"
label(data$comments_fws)="Comments"
label(data$fever_without_source_study_complete)="Complete?"
label(data$qc_stage)="Current stage of quality control"
label(data$qc_date)="Date of quality control stage change"
label(data$first_analysis)="First Analysis"
label(data$quality_control_complete)="Complete?"
# #Setting Units
#
# #Setting Factors(will create new variable for factors - cambiar a que no cree nuevas variables)
## data$hospital = factor(data$hospital,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","15"))
data$hospital = factor(data$hospital,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","15","16","17","18","19","20","21","22"))
data$center_id_complete = factor(data$center_id_complete,levels=c("0","1","2"))
data$sex = factor(data$sex,levels=c("1","2","3"))
data$last_15 = factor(data$last_15,levels=c("1","2","3"))
data$demographics_complete = factor(data$demographics_complete,levels=c("0","1","2"))
data$symptoms_epi_travel = factor(data$symptoms_epi_travel,levels=c("1","2","3"))
data$symptoms_epi_physical = factor(data$symptoms_epi_physical,levels=c("1","2","3"))
data$symptoms_epi_healthfac = factor(data$symptoms_epi_healthfac,levels=c("1","2","3"))
data$symptoms_epi_animal = factor(data$symptoms_epi_animal,levels=c("1","2","3"))
data$symptoms_epi_comm = factor(data$symptoms_epi_comm,levels=c("1","2","3"))
data$contact___1 = factor(data$contact___1,levels=c("0","1"))
data$contact___2 = factor(data$contact___2,levels=c("0","1"))
data$contact___3 = factor(data$contact___3,levels=c("0","1"))
data$contact___4 = factor(data$contact___4,levels=c("0","1"))
data$inclusion_criteria_complete = factor(data$inclusion_criteria_complete,levels=c("0","1","2"))
data$anamnesis_complete = factor(data$anamnesis_complete,levels=c("0","1","2"))
data$comorb = factor(data$comorb,levels=c("1","0"))
data$chroniccard_mhyn = factor(data$chroniccard_mhyn,levels=c("1","2","3"))
data$hypertension_mhyn = factor(data$hypertension_mhyn,levels=c("1","2","3"))
data$chronicpul_mhyn = factor(data$chronicpul_mhyn,levels=c("1","2","3"))
data$asthma_mhyn = factor(data$asthma_mhyn,levels=c("1","2","3"))
data$tb_mhyn = factor(data$tb_mhyn,levels=c("1","2","3"))
data$resp_inf_mhyn = factor(data$resp_inf_mhyn,levels=c("1","2","3"))
data$renal_mhyn = factor(data$renal_mhyn,levels=c("1","2","3"))
data$modliver_mhyn = factor(data$modliver_mhyn,levels=c("1","2","3"))
data$mildliv_mhyn = factor(data$mildliv_mhyn,levels=c("1","2","3"))
data$chronicneu_mhyn = factor(data$chronicneu_mhyn,levels=c("1","2","3"))
data$malignantneo_mhyn = factor(data$malignantneo_mhyn,levels=c("1","2","3"))
data$chronhaemo_mhyn = factor(data$chronhaemo_mhyn,levels=c("1","2","3"))
data$aidshiv_mhyn = factor(data$aidshiv_mhyn,levels=c("1","2","3"))
data$obesity_mhyn = factor(data$obesity_mhyn,levels=c("1","2","3"))
data$diabetiscomp_mhyn = factor(data$diabetiscomp_mhyn,levels=c("1","2","3"))
data$diabetes_mhyn = factor(data$diabetes_mhyn,levels=c("1","2","3"))
data$inflammatory_mhyr = factor(data$inflammatory_mhyr,levels=c("1","2","3"))
data$rheumatology_mhyr = factor(data$rheumatology_mhyr,levels=c("1","2","3"))
data$kawa_mhyn = factor(data$kawa_mhyn,levels=c("1","2","3"))
data$kawa_fam_mhyn = factor(data$kawa_fam_mhyn,levels=c("1","2","3"))
data$dementia_mhyn = factor(data$dementia_mhyn,levels=c("1","2","3"))
data$malnutrition_mhyn = factor(data$malnutrition_mhyn,levels=c("1","2","3"))
data$other_mhyn = factor(data$other_mhyn,levels=c("1","2","3"))
data$smoking_mhyn = factor(data$smoking_mhyn,levels=c("1","2","3"))
data$immunosupressors = factor(data$immunosupressors,levels=c("1","0"))
data$comorbidities_complete = factor(data$comorbidities_complete,levels=c("0","1","2"))
data$influenza_full_regimen = factor(data$influenza_full_regimen,levels=c("1","0"))
data$apsc_vcageind = factor(data$apsc_vcageind,levels=c("1","2","3"))
data$vaccines_complete = factor(data$vaccines_complete,levels=c("0","1","2"))
data$anthropometry_complete = factor(data$anthropometry_complete,levels=c("0","1","2"))
data$dehydr = factor(data$dehydr,levels=c("1","2","3"))
data$fever_ceoccur_v2 = factor(data$fever_ceoccur_v2,levels=c("1","2","3"))
data$cough_ceoccur_v2 = factor(data$cough_ceoccur_v2,levels=c("1","2","3"))
data$sorethroat_ceoccur_v2 = factor(data$sorethroat_ceoccur_v2,levels=c("1","2","3"))
data$runnynose_ceoccur_v2 = factor(data$runnynose_ceoccur_v2,levels=c("1","2","3"))
data$wheeze_ceoccur_v2 = factor(data$wheeze_ceoccur_v2,levels=c("1","2","3"))
data$chestpain_ceoccur_v2 = factor(data$chestpain_ceoccur_v2,levels=c("1","2","3"))
data$myalgia_ceoccur_v2 = factor(data$myalgia_ceoccur_v2,levels=c("1","2","3"))
data$jointpain_ceoccur_v2 = factor(data$jointpain_ceoccur_v2,levels=c("1","2","3"))
data$fatigue_ceoccur_v2 = factor(data$fatigue_ceoccur_v2,levels=c("1","2","3"))
data$shortbreath_ceoccur_v2 = factor(data$shortbreath_ceoccur_v2,levels=c("1","2","3"))
data$lowerchest_ceoccur_v2 = factor(data$lowerchest_ceoccur_v2,levels=c("1","2","3"))
data$headache_ceoccur_v2 = factor(data$headache_ceoccur_v2,levels=c("1","2","3"))
data$confusion_ceoccur_v2 = factor(data$confusion_ceoccur_v2,levels=c("1","2","3"))
data$seizures_cecoccur_v2 = factor(data$seizures_cecoccur_v2,levels=c("1","2","3"))
data$abdopain_ceoccur_v2 = factor(data$abdopain_ceoccur_v2,levels=c("1","2","3"))
data$vomit_ceoccur_v2 = factor(data$vomit_ceoccur_v2,levels=c("1","2","3"))
data$diarrhoea_ceoccur_v2 = factor(data$diarrhoea_ceoccur_v2,levels=c("1","2","3"))
data$conjunct_ceoccur_v2 = factor(data$conjunct_ceoccur_v2,levels=c("1","2","3"))
data$oral_inf = factor(data$oral_inf,levels=c("1","2","3"))
data$pale_skin = factor(data$pale_skin,levels=c("1","2","3"))
data$rash_ceoccur_v2 = factor(data$rash_ceoccur_v2,levels=c("1","2","3"))
data$skinulcers_ceoccur_v2 = factor(data$skinulcers_ceoccur_v2,levels=c("1","2","3"))
data$peri_inf = factor(data$peri_inf,levels=c("1","2","3"))
data$lymp_ceoccur_v2 = factor(data$lymp_ceoccur_v2,levels=c("1","2","3"))
data$bleed_ceoccur_v2 = factor(data$bleed_ceoccur_v2,levels=c("1","2","3"))
data$cold_hands = factor(data$cold_hands,levels=c("1","2","3"))
data$cap_refill = factor(data$cap_refill,levels=c("1","2","3"))
data$sw_joints = factor(data$sw_joints,levels=c("1","2","3"))
data$st_neck = factor(data$st_neck,levels=c("1","2","3"))
data$hypo_flop = factor(data$hypo_flop,levels=c("1","2","3"))
data$paralysis = factor(data$paralysis,levels=c("1","2","3"))
data$shock = factor(data$shock,levels=c("1","2","3"))
data$sens_alt = factor(data$sens_alt,levels=c("1","2","3"))
data$admission_signs_and_symptoms_complete = factor(data$admission_signs_and_symptoms_complete,levels=c("0","1","2"))
data$blood_tests_complete = factor(data$blood_tests_complete,levels=c("0","1","2"))
data$pcr_cov2_1 = factor(data$pcr_cov2_1,levels=c("1","2","3","4"))
data$pcr_cov2_2 = factor(data$pcr_cov2_2,levels=c("1","2","3","4"))
data$pcr_cov2_3 = factor(data$pcr_cov2_3,levels=c("1","2","3","4"))
data$pcr_cov2_4 = factor(data$pcr_cov2_4,levels=c("1","2","3","4"))
data$rapid_ag_test_covid___1 = factor(data$rapid_ag_test_covid___1,levels=c("0","1"))
data$rapid_ag_test_covid___2 = factor(data$rapid_ag_test_covid___2,levels=c("0","1"))
data$rapid_ag_test_covid_1 = factor(data$rapid_ag_test_covid_1,levels=c("1","2"))
data$rapid_ag_test_covid_2 = factor(data$rapid_ag_test_covid_2,levels=c("1","2"))
data$virus_obtained_pcr_16 = factor(data$virus_obtained_pcr_16,levels=c("1","0"))
data$pcr_types_virus_sr___1 = factor(data$pcr_types_virus_sr___1,levels=c("0","1"))
data$pcr_types_virus_sr___2 = factor(data$pcr_types_virus_sr___2,levels=c("0","1"))
data$pcr_types_virus_sr___3 = factor(data$pcr_types_virus_sr___3,levels=c("0","1"))
data$pcr_types_virus_sr___4 = factor(data$pcr_types_virus_sr___4,levels=c("0","1"))
data$pcr_types_virus_sr___5 = factor(data$pcr_types_virus_sr___5,levels=c("0","1"))
data$pcr_types_virus_sr___6 = factor(data$pcr_types_virus_sr___6,levels=c("0","1"))
data$pcr_types_virus_sr___7 = factor(data$pcr_types_virus_sr___7,levels=c("0","1"))
data$pcr_types_virus_sr___8 = factor(data$pcr_types_virus_sr___8,levels=c("0","1"))
data$pcr_types_virus_sr___9 = factor(data$pcr_types_virus_sr___9,levels=c("0","1"))
data$pcr_types_virus_sr___10 = factor(data$pcr_types_virus_sr___10,levels=c("0","1"))
data$pcr_types_virus_sr___11 = factor(data$pcr_types_virus_sr___11,levels=c("0","1"))
data$pcr_types_virus_sr___12 = factor(data$pcr_types_virus_sr___12,levels=c("0","1"))
data$pcr_types_virus_sr___13 = factor(data$pcr_types_virus_sr___13,levels=c("0","1"))
data$pcr_types_virus_sr___14 = factor(data$pcr_types_virus_sr___14,levels=c("0","1"))
data$pcr_types_virus_sr___15 = factor(data$pcr_types_virus_sr___15,levels=c("0","1"))
data$pcr_types_virus_sr___16 = factor(data$pcr_types_virus_sr___16,levels=c("0","1"))
data$pcr_atipical_sr = factor(data$pcr_atipical_sr,levels=c("1","0"))
data$pcr_mn_sr = factor(data$pcr_mn_sr,levels=c("1","2","3","4"))
data$pcr_cn_sr = factor(data$pcr_cn_sr,levels=c("1","2","3","4"))
data$pcr_hib_sr = factor(data$pcr_hib_sr,levels=c("1","2","3","4"))
data$pcr_leg_sr = factor(data$pcr_leg_sr,levels=c("1","2","3","4"))
data$pcr_bordetella_sr = factor(data$pcr_bordetella_sr,levels=c("1","2","3","4"))
data$anti_influenza = factor(data$anti_influenza,levels=c("1","2","3"))
data$anti_rsv = factor(data$anti_rsv,levels=c("1","2","3"))
data$res_samples = factor(data$res_samples,levels=c("1","0"))
data$respiratory_secretion_microbiology_complete = factor(data$respiratory_secretion_microbiology_complete,levels=c("0","1","2"))
data$first_sr_sc2 = factor(data$first_sr_sc2,levels=c("1","0","2","3"))
data$first_sr_sc2_type = factor(data$first_sr_sc2_type,levels=c("1","2","3","4"))
data$igm_sc2_1 = factor(data$igm_sc2_1,levels=c("1","2","3","4"))
data$igg_sc2_1 = factor(data$igg_sc2_1,levels=c("1","2","3","4"))
data$second_sr_sc2 = factor(data$second_sr_sc2,levels=c("1","0","2","3"))
data$second_sr_sc2_type = factor(data$second_sr_sc2_type,levels=c("1","2","3","4"))
data$igm_sc2_2 = factor(data$igm_sc2_2,levels=c("1","2","3","4"))
data$igg_sc2_2 = factor(data$igg_sc2_2,levels=c("1","2","3","4"))
data$blood_culture = factor(data$blood_culture,levels=c("1","0"))
data$probable_bacterial_etiology_hemoculture = factor(data$probable_bacterial_etiology_hemoculture,levels=c("1","2","3","4"))
data$other_bacteria_hemoculture = factor(data$other_bacteria_hemoculture,levels=c("1","0"))
data$first_sr_atipical = factor(data$first_sr_atipical,levels=c("1","0","2","3"))
data$serology1_igm_mn = factor(data$serology1_igm_mn,levels=c("1","2","3","4"))
data$serology1_igg_mn = factor(data$serology1_igg_mn,levels=c("1","2","3","4"))
data$serology1_igm_cn = factor(data$serology1_igm_cn,levels=c("1","2","3","4"))
data$serology1_igg_cn = factor(data$serology1_igg_cn,levels=c("1","2","3","4"))
data$second_sr_atipical = factor(data$second_sr_atipical,levels=c("1","0","2","3"))
data$serology2_igm_mn = factor(data$serology2_igm_mn,levels=c("1","2","3","4"))
data$serology2_igg_mn = factor(data$serology2_igg_mn,levels=c("1","2","3","4"))
data$serology2_igm_cn = factor(data$serology2_igm_cn,levels=c("1","2","3","4"))
data$serology2_igg_cn = factor(data$serology2_igg_cn,levels=c("1","2","3","4"))
data$seroconversion_mn = factor(data$seroconversion_mn,levels=c("1","2","3","4"))
data$blood_samples = factor(data$blood_samples,levels=c("1","0"))
data$plasma_samples = factor(data$plasma_samples,levels=c("1","0"))
data$blood_microbiology_complete = factor(data$blood_microbiology_complete,levels=c("0","1","2"))
data$codetection = factor(data$codetection,levels=c("1","2","3","4"))
data$codetecion_type = factor(data$codetecion_type,levels=c("1","2"))
data$codetecion_complete = factor(data$codetecion_complete,levels=c("0","1","2"))
data$thoracentesis_done = factor(data$thoracentesis_done,levels=c("1","0"))
data$ag_pneumo_pf = factor(data$ag_pneumo_pf,levels=c("1","2","3"))
data$pcr_pneumo_pf = factor(data$pcr_pneumo_pf,levels=c("1","2","3"))
data$culture_pf = factor(data$culture_pf,levels=c("1","2"))
data$cultured_bacteria_pf = factor(data$cultured_bacteria_pf,levels=c("1","2","3","4","5"))
data$pleural_fluid_microbiology_complete = factor(data$pleural_fluid_microbiology_complete,levels=c("0","1","2"))
data$oxygen_therapy = factor(data$oxygen_therapy,levels=c("1","0"))
data$hft = factor(data$hft,levels=c("1","0"))
data$cpap = factor(data$cpap,levels=c("1","0"))
data$picu_admission = factor(data$picu_admission,levels=c("1","0"))
data$mechanical_ventilation = factor(data$mechanical_ventilation,levels=c("1","0"))
data$nimv = factor(data$nimv,levels=c("1","0"))
data$imv = factor(data$imv,levels=c("1","0"))
data$evolution_complete = factor(data$evolution_complete,levels=c("0","1","2"))
data$complications = factor(data$complications,levels=c("1","0"))
data$pleural_effusion = factor(data$pleural_effusion,levels=c("1","0"))
data$effusion_type = factor(data$effusion_type,levels=c("1","2"))
data$corticosteroids = factor(data$corticosteroids,levels=c("1","0"))
data$pleural_drainage = factor(data$pleural_drainage,levels=c("1","0"))
data$drainage_type = factor(data$drainage_type,levels=c("1","2","3"))
data$pneumatocele_abscess = factor(data$pneumatocele_abscess,levels=c("1","0"))
data$pneumothorax = factor(data$pneumothorax,levels=c("1","0"))
data$cardio_comp = factor(data$cardio_comp,levels=c("1","0"))
data$cardio_comp_myoc = factor(data$cardio_comp_myoc,levels=c("1","0"))
data$cardio_comp_peri = factor(data$cardio_comp_peri,levels=c("1","0"))
data$cardio_comp_valve = factor(data$cardio_comp_valve,levels=c("1","0"))
data$cardio_comp_arry = factor(data$cardio_comp_arry,levels=c("1","0"))
data$cardio_comp_cor = factor(data$cardio_comp_cor,levels=c("1","0"))
data$cardio_comp_ane = factor(data$cardio_comp_ane,levels=c("1","0"))
data$sepsis = factor(data$sepsis,levels=c("1","0"))
data$renal_failure = factor(data$renal_failure,levels=c("1","0"))
data$kawa = factor(data$kawa,levels=c("1","0"))
data$complications_complete = factor(data$complications_complete,levels=c("0","1","2"))
data$xray_result_1 = factor(data$xray_result_1,levels=c("1","2","3"))
data$x_ray_1_reported_by___1 = factor(data$x_ray_1_reported_by___1,levels=c("0","1"))
data$x_ray_1_reported_by___2 = factor(data$x_ray_1_reported_by___2,levels=c("0","1"))
data$x_ray_1_reported_by___3 = factor(data$x_ray_1_reported_by___3,levels=c("0","1"))
data$x_ray_1_result_ext = factor(data$x_ray_1_result_ext,levels=c("1","2","3"))
data$xray_result_2 = factor(data$xray_result_2,levels=c("1","2","3"))
data$x_ray_2_reported_by___1 = factor(data$x_ray_2_reported_by___1,levels=c("0","1"))
data$x_ray_2_reported_by___2 = factor(data$x_ray_2_reported_by___2,levels=c("0","1"))
data$x_ray_2_reported_by___3 = factor(data$x_ray_2_reported_by___3,levels=c("0","1"))
data$x_ray_2_result_ext = factor(data$x_ray_2_result_ext,levels=c("1","2","3"))
data$xray_result_3 = factor(data$xray_result_3,levels=c("1","2","3"))
data$x_ray_3_reported_by___1 = factor(data$x_ray_3_reported_by___1,levels=c("0","1"))
data$x_ray_3_reported_by___2 = factor(data$x_ray_3_reported_by___2,levels=c("0","1"))
data$x_ray_3_reported_by___3 = factor(data$x_ray_3_reported_by___3,levels=c("0","1"))
data$x_ray_3_result_ext = factor(data$x_ray_3_result_ext,levels=c("1","2","3"))
data$cardiac_img = factor(data$cardiac_img,levels=c("1","2","3"))
data$radiology_complete = factor(data$radiology_complete,levels=c("0","1","2"))
data$oro_fluids = factor(data$oro_fluids,levels=c("1","2","3"))
data$iv_fluids = factor(data$iv_fluids,levels=c("1","2","3"))
data$antiviral_cmyn = factor(data$antiviral_cmyn,levels=c("1","2","3"))
data$antiviral_cmtrt___1 = factor(data$antiviral_cmtrt___1,levels=c("0","1"))
data$antiviral_cmtrt___2 = factor(data$antiviral_cmtrt___2,levels=c("0","1"))
data$antiviral_cmtrt___3 = factor(data$antiviral_cmtrt___3,levels=c("0","1"))
data$antiviral_cmtrt___4 = factor(data$antiviral_cmtrt___4,levels=c("0","1"))
data$antiviral_cmtrt___5 = factor(data$antiviral_cmtrt___5,levels=c("0","1"))
data$antiviral_cmtrt___6 = factor(data$antiviral_cmtrt___6,levels=c("0","1"))
data$antiviral_cmtrt___7 = factor(data$antiviral_cmtrt___7,levels=c("0","1"))
data$antiviral_cmtrt___8 = factor(data$antiviral_cmtrt___8,levels=c("0","1"))
data$antiviral_cmtrt___10 = factor(data$antiviral_cmtrt___10,levels=c("0","1"))
data$antiviral_cmtrt___11 = factor(data$antiviral_cmtrt___11,levels=c("0","1"))
data$antiviral_cmtrt___9 = factor(data$antiviral_cmtrt___9,levels=c("0","1"))
data$antibiotic_cmyn = factor(data$antibiotic_cmyn,levels=c("1","2","3"))
data$iv_ab = factor(data$iv_ab,levels=c("1","2","3"))
data$type_iv_ab___0 = factor(data$type_iv_ab___0,levels=c("0","1"))
data$type_iv_ab___1 = factor(data$type_iv_ab___1,levels=c("0","1"))
data$type_iv_ab___2 = factor(data$type_iv_ab___2,levels=c("0","1"))
data$type_iv_ab___3 = factor(data$type_iv_ab___3,levels=c("0","1"))
data$type_iv_ab___4 = factor(data$type_iv_ab___4,levels=c("0","1"))
data$type_iv_ab___5 = factor(data$type_iv_ab___5,levels=c("0","1"))
data$type_iv_ab___6 = factor(data$type_iv_ab___6,levels=c("0","1"))
data$type_iv_ab___9 = factor(data$type_iv_ab___9,levels=c("0","1"))
data$type_iv_ab___8 = factor(data$type_iv_ab___8,levels=c("0","1"))
data$type_iv_ab___7 = factor(data$type_iv_ab___7,levels=c("0","1"))
data$o_ab = factor(data$o_ab,levels=c("1","0"))
data$type_o_ab___1 = factor(data$type_o_ab___1,levels=c("0","1"))
data$type_o_ab___2 = factor(data$type_o_ab___2,levels=c("0","1"))
data$type_o_ab___3 = factor(data$type_o_ab___3,levels=c("0","1"))
data$type_o_ab___4 = factor(data$type_o_ab___4,levels=c("0","1"))
data$type_o_ab___5 = factor(data$type_o_ab___5,levels=c("0","1"))
data$type_o_ab___6 = factor(data$type_o_ab___6,levels=c("0","1"))
data$type_o_ab___7 = factor(data$type_o_ab___7,levels=c("0","1"))
data$type_o_ab___8 = factor(data$type_o_ab___8,levels=c("0","1"))
data$corticost_cmyn = factor(data$corticost_cmyn,levels=c("1","2","3"))
data$corticost_cmroute = factor(data$corticost_cmroute,levels=c("1","2","3"))
data$anti_inflammatory___1 = factor(data$anti_inflammatory___1,levels=c("0","1"))
data$anti_inflammatory___2 = factor(data$anti_inflammatory___2,levels=c("0","1"))
data$other_anti_inflammatory = factor(data$other_anti_inflammatory,levels=c("1","2","3"))
data$iv_imglob = factor(data$iv_imglob,levels=c("1","2","3"))
data$imod = factor(data$imod,levels=c("1","2","3"))
data$sys_anticoag = factor(data$sys_anticoag,levels=c("1","2","3"))
data$anti_mal = factor(data$anti_mal,levels=c("1","2","3"))
data$antifung_cmyn = factor(data$antifung_cmyn,levels=c("1","2","3"))
data$experimental = factor(data$experimental,levels=c("1","2","3"))
data$other_sc2_treatments = factor(data$other_sc2_treatments,levels=c("1","2","3"))
data$vasopressors = factor(data$vasopressors,levels=c("1","2","3"))
data$vasopressors_type___1 = factor(data$vasopressors_type___1,levels=c("0","1"))
data$vasopressors_type___2 = factor(data$vasopressors_type___2,levels=c("0","1"))
data$vasopressors_type___3 = factor(data$vasopressors_type___3,levels=c("0","1"))
data$vasopressors_type___4 = factor(data$vasopressors_type___4,levels=c("0","1"))
data$vasopressors_type___5 = factor(data$vasopressors_type___5,levels=c("0","1"))
data$vasopressors_type___6 = factor(data$vasopressors_type___6,levels=c("0","1"))
data$ecmo = factor(data$ecmo,levels=c("1","2","3"))
data$blood_trans = factor(data$blood_trans,levels=c("1","2","3"))
data$medication_complete = factor(data$medication_complete,levels=c("0","1","2"))
data$dsterm = factor(data$dsterm,levels=c("1","2","3","4","5","8","6","7"))
data$excluded_reason = factor(data$excluded_reason,levels=c("1","2","3"))
data$final_dx_1 = factor(data$final_dx_1,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
data$related_1 = factor(data$related_1,levels=c("1","2"))
data$final_dx_2 = factor(data$final_dx_2,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
data$related_2 = factor(data$related_2,levels=c("1","2","3"))
data$final_dx_3 = factor(data$final_dx_3,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
data$final_dx_4 = factor(data$final_dx_4,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
data$final_dx_5 = factor(data$final_dx_5,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
data$final_dx_6 = factor(data$final_dx_6,levels=c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","45","46","47"))
data$related_3 = factor(data$related_3,levels=c("1","2","3"))
data$outcome_complete = factor(data$outcome_complete,levels=c("0","1","2"))
data$spirometry_complete = factor(data$spirometry_complete,levels=c("0","1","2"))
data$fever_ws = factor(data$fever_ws,levels=c("1","0"))
data$lumbar_punc = factor(data$lumbar_punc,levels=c("1","0"))
data$csf_bacteria = factor(data$csf_bacteria,levels=c("1","0"))
data$csf_vhs = factor(data$csf_vhs,levels=c("1","0","2"))
data$csf_enterovirus = factor(data$csf_enterovirus,levels=c("1","0","2"))
data$csf_sarscov2 = factor(data$csf_sarscov2,levels=c("1","0","2"))
data$urine_collection = factor(data$urine_collection,levels=c("1","2","3","4","5"))
data$urine_dipstik = factor(data$urine_dipstik,levels=c("1","2","3","4","5"))
data$urine_culture = factor(data$urine_culture,levels=c("1","0","2"))
data$fever_without_source_study_complete = factor(data$fever_without_source_study_complete,levels=c("0","1","2"))
data$qc_stage = factor(data$qc_stage,levels=c("0","1","2","3","4"))
data$first_analysis = factor(data$first_analysis,levels=c("1","0"))
data$quality_control_complete = factor(data$quality_control_complete,levels=c("0","1","2"))

## levels(data$hospital)=c("Clínica Infantil Colsubsidio (CIC)","Hospital Universitario Fundación Santa Fé de Bogotá (HUFSFB)","Instituto Roosevelt (IR)","Ministerio de Salud de Colombia","Universidad de los Andes","Hospital de Nariño","San José Centro","San José Infantil","Hospital Militar","Clínica Colsanitas S.A. Sede Clínica Pediatrica","Clínica Colsanitas S.A. Sede Santa María del Lago","Clínica Colsanitas S.A. Sede Clínica Reina Sofía","Clínica Colsanitas S.A. Sede Clínica Universitaria 14, Colombia","Hospital Regional de la Orinoquia")
#
levels(data$hospital)=c("Clínica Infantil Colsubsidio (CIC)","Hospital Universitario Fundación Santa Fe de Bogotá (HUFSFB)","Instituto Roosevelt (IR)","Ministerio de Salud de Colombia","Universidad de los Andes","Hospital de Nariño","San José Centro","San José Infantil","Hospital Militar","Clínica Colsanitas Pediátrica","Clínica Colsanitas S.A. Sede Santa María del Lago","Clinica Colsanitas Reina Sofia","Clinica Colsanitas Universitaria Colombia","Hospital Regional de la Orinoquia","Clinica Los Cobos","Clinica Materno Infantil San Luis","Clinica del Rosario","Clinica SOMA","Hospital Universitario Fundacion Valle del Lili","Fundacion San Vicente de Paul (Medellin)","Centro Medico Crecer (Cartagena)")



levels(data$center_id_complete)=c("Incomplete","Unverified","Complete")
levels(data$sex)=c("Male","Female","Not specified")
levels(data$last_15)=c("Yes","No","Unknown")
levels(data$demographics_complete)=c("Incomplete","Unverified","Complete")
levels(data$symptoms_epi_travel)=c("Yes","No","Unknown")
levels(data$symptoms_epi_physical)=c("Yes","No","Unknown")
levels(data$symptoms_epi_healthfac)=c("Yes","No","Unknown")
levels(data$symptoms_epi_animal)=c("Yes","No","Unknown")
levels(data$symptoms_epi_comm)=c("Yes","No","Unknown")
levels(data$contact___1)=c("Unchecked","Checked")
levels(data$contact___2)=c("Unchecked","Checked")
levels(data$contact___3)=c("Unchecked","Checked")
levels(data$contact___4)=c("Unchecked","Checked")
levels(data$inclusion_criteria_complete)=c("Incomplete","Unverified","Complete")
levels(data$anamnesis_complete)=c("Incomplete","Unverified","Complete")
levels(data$comorb)=c("Yes","No")
levels(data$chroniccard_mhyn)=c("Yes","No","Unknown")
levels(data$hypertension_mhyn)=c("Yes","No","Unknown")
levels(data$chronicpul_mhyn)=c("Yes","No","Unknown")
levels(data$asthma_mhyn)=c("Yes","No","Unknown")
levels(data$tb_mhyn)=c("Yes","No","Unknown")
levels(data$resp_inf_mhyn)=c("Yes","No","Unknown")
levels(data$renal_mhyn)=c("Yes","No","Unknown")
levels(data$modliver_mhyn)=c("Yes","No","Unknown")
levels(data$mildliv_mhyn)=c("Yes","No","Unknown")
levels(data$chronicneu_mhyn)=c("Yes","No","Unknown")
levels(data$malignantneo_mhyn)=c("Yes","No","Unknown")
levels(data$chronhaemo_mhyn)=c("Yes","No","Unknown")
levels(data$aidshiv_mhyn)=c("Yes","No","Unknown")
levels(data$obesity_mhyn)=c("Yes","No","Unknown")
levels(data$diabetiscomp_mhyn)=c("Yes","No","Unknown")
levels(data$diabetes_mhyn)=c("Yes","No","Unknown")
levels(data$inflammatory_mhyr)=c("Yes","No","Unknown")
levels(data$rheumatology_mhyr)=c("Yes","No","Unknown")
levels(data$kawa_mhyn)=c("Yes","No","Unknown")
levels(data$kawa_fam_mhyn)=c("Yes","No","Unknown")
levels(data$dementia_mhyn)=c("Yes","No","Unknown")
levels(data$malnutrition_mhyn)=c("Yes","No","Unknown")
levels(data$other_mhyn)=c("Yes","No","Unknown")
levels(data$smoking_mhyn)=c("Yes","Never Smoker","Former Smoker")
levels(data$immunosupressors)=c("Yes","No")
levels(data$comorbidities_complete)=c("Incomplete","Unverified","Complete")
levels(data$influenza_full_regimen)=c("Yes","No")
levels(data$apsc_vcageind)=c("Yes","No","Unknown")
levels(data$vaccines_complete)=c("Incomplete","Unverified","Complete")
levels(data$anthropometry_complete)=c("Incomplete","Unverified","Complete")
levels(data$dehydr)=c("Severe","Some","None")
levels(data$fever_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$cough_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$sorethroat_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$runnynose_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$wheeze_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$chestpain_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$myalgia_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$jointpain_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$fatigue_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$shortbreath_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$lowerchest_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$headache_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$confusion_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$seizures_cecoccur_v2)=c("Yes","No","Unknown")
levels(data$abdopain_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$vomit_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$diarrhoea_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$conjunct_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$oral_inf)=c("Yes","No","Unknown")
levels(data$pale_skin)=c("Yes","No","Unknown")
levels(data$rash_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$skinulcers_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$peri_inf)=c("Yes","No","Unknown")
levels(data$lymp_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$bleed_ceoccur_v2)=c("Yes","No","Unknown")
levels(data$cold_hands)=c("Yes","No","Unknown")
levels(data$cap_refill)=c("Yes","No","Unknown")
levels(data$sw_joints)=c("Yes","No","Unknown")
levels(data$st_neck)=c("Yes","No","Unknown")
levels(data$hypo_flop)=c("Yes","No","Unknown")
levels(data$paralysis)=c("Yes","No","Unknown")
levels(data$shock)=c("Yes","No","Unknown")
levels(data$sens_alt)=c("Yes","No","Unknown")
levels(data$admission_signs_and_symptoms_complete)=c("Incomplete","Unverified","Complete")
levels(data$blood_tests_complete)=c("Incomplete","Unverified","Complete")
levels(data$pcr_cov2_1)=c("Positive","Negative","Pending","Unavailable")
levels(data$pcr_cov2_2)=c("Positive","Negative","Pending","Unavailable")
levels(data$pcr_cov2_3)=c("Positive","Negative","Pending","Unavailable")
levels(data$pcr_cov2_4)=c("Positive","Negative","Pending","Unavailable")
levels(data$rapid_ag_test_covid___1)=c("Unchecked","Checked")
levels(data$rapid_ag_test_covid___2)=c("Unchecked","Checked")
levels(data$rapid_ag_test_covid_1)=c("Positive","Negative")
levels(data$rapid_ag_test_covid_2)=c("Positive","Negative")
levels(data$virus_obtained_pcr_16)=c("Yes","No")
levels(data$pcr_types_virus_sr___1)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___2)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___3)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___4)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___5)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___6)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___7)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___8)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___9)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___10)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___11)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___12)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___13)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___14)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___15)=c("Unchecked","Checked")
levels(data$pcr_types_virus_sr___16)=c("Unchecked","Checked")
levels(data$pcr_atipical_sr)=c("Yes","No")
levels(data$pcr_mn_sr)=c("Positive","Negative","Pending","Unavailable")
levels(data$pcr_cn_sr)=c("Positive","Negative","Pending","Unavailable")
levels(data$pcr_hib_sr)=c("Positive","Negative","Pending","Unavailable")
levels(data$pcr_leg_sr)=c("Positive","Negative","Pending","Unavailable")
levels(data$pcr_bordetella_sr)=c("Positive","Negative","Pending","Unavailable")
levels(data$anti_influenza)=c("Positive","Negative","Not performed")
levels(data$anti_rsv)=c("Positive","Negative","Not performed")
levels(data$res_samples)=c("Yes","No")
levels(data$respiratory_secretion_microbiology_complete)=c("Incomplete","Unverified","Complete")
levels(data$first_sr_sc2)=c("Yes","No","Sample collection pending","Results pending")
levels(data$first_sr_sc2_type)=c("Rapid test","ELISA","Neutralization test","Other")
levels(data$igm_sc2_1)=c("Positive","Negative","Pending","Unavailable")
levels(data$igg_sc2_1)=c("Positive","Negative","Pending","Unavailable")
levels(data$second_sr_sc2)=c("Yes","No","Sample collection pending","Results pending")
levels(data$second_sr_sc2_type)=c("Rapid test","ELISA","Neutralization test","Other")
levels(data$igm_sc2_2)=c("Positive","Negative","Pending","Unavailable")
levels(data$igg_sc2_2)=c("Positive","Negative","Pending","Unavailable")
levels(data$blood_culture)=c("Yes","No")
levels(data$probable_bacterial_etiology_hemoculture)=c("S. pneumoniae","S. aureus","S. pyogenes","Other (specify)")
levels(data$other_bacteria_hemoculture)=c("Yes","No")
levels(data$first_sr_atipical)=c("Yes","No","Sample collection pending","Results pending")
levels(data$serology1_igm_mn)=c("Positive","Negative","Pending","Unavailable")
levels(data$serology1_igg_mn)=c("Positive","Negative","Pending","Unavailable")
levels(data$serology1_igm_cn)=c("Positive","Negative","Pending","Unavailable")
levels(data$serology1_igg_cn)=c("Positive","Negative","Pending","Unavailable")
levels(data$second_sr_atipical)=c("Yes","No","Sample collection pending","Results pending")
levels(data$serology2_igm_mn)=c("Positive","Negative","Pending","Unavailable")
levels(data$serology2_igg_mn)=c("Positive","Negative","Pending","Unavailable")
levels(data$serology2_igm_cn)=c("Positive","Negative","Pending","Unavailable")
levels(data$serology2_igg_cn)=c("Positive","Negative","Pending","Unavailable")
levels(data$seroconversion_mn)=c("Yes","No","Pending","Unavailable")
levels(data$blood_samples)=c("Yes","No")
levels(data$plasma_samples)=c("Yes","No")
levels(data$blood_microbiology_complete)=c("Incomplete","Unverified","Complete")
levels(data$codetection)=c("Yes","No","Pending","Unknown due to lack of microbiological data")
levels(data$codetecion_type)=c("Virus-Virus","Virus-Bacteria")
levels(data$codetecion_complete)=c("Incomplete","Unverified","Complete")
levels(data$thoracentesis_done)=c("Yes","No")
levels(data$ag_pneumo_pf)=c("Positive","Negative","Not performed")
levels(data$pcr_pneumo_pf)=c("Positive","Negative","Not performed")
levels(data$culture_pf)=c("Positive","Negative")
levels(data$cultured_bacteria_pf)=c("Pneumococcus","S. pyogenes","S. aureus","Haemophilus influenzae","Other")
levels(data$pleural_fluid_microbiology_complete)=c("Incomplete","Unverified","Complete")
levels(data$oxygen_therapy)=c("Yes","No")
levels(data$hft)=c("Yes","No")
levels(data$cpap)=c("Yes","No")
levels(data$picu_admission)=c("Yes","No")
levels(data$mechanical_ventilation)=c("Yes","No")
levels(data$nimv)=c("Yes","No")
levels(data$imv)=c("Yes","No")
levels(data$evolution_complete)=c("Incomplete","Unverified","Complete")
levels(data$complications)=c("Yes","No")
levels(data$pleural_effusion)=c("Yes","No")
levels(data$effusion_type)=c("Not complicated","Complicated (pH< 7 and/or partitions)")
levels(data$corticosteroids)=c("Yes","No")
levels(data$pleural_drainage)=c("Yes","No")
levels(data$drainage_type)=c("Pleural tube","VATS","Evacuating thoracentesis only")
levels(data$pneumatocele_abscess)=c("Yes","No")
levels(data$pneumothorax)=c("Yes","No")
levels(data$cardio_comp)=c("Yes","No")
levels(data$cardio_comp_myoc)=c("Yes","No")
levels(data$cardio_comp_peri)=c("Yes","No")
levels(data$cardio_comp_valve)=c("Yes","No")
levels(data$cardio_comp_arry)=c("Yes","No")
levels(data$cardio_comp_cor)=c("Yes","No")
levels(data$cardio_comp_ane)=c("Yes","No")
levels(data$sepsis)=c("Yes","No")
levels(data$renal_failure)=c("Yes","No")
levels(data$kawa)=c("Yes","No")
levels(data$complications_complete)=c("Incomplete","Unverified","Complete")
levels(data$xray_result_1)=c("Condensation","Other infiltrates","Normal")
levels(data$x_ray_1_reported_by___1)=c("Unchecked","Checked")
levels(data$x_ray_1_reported_by___2)=c("Unchecked","Checked")
levels(data$x_ray_1_reported_by___3)=c("Unchecked","Checked")
levels(data$x_ray_1_result_ext)=c("Condensation","Other infiltrates","Normal")
levels(data$xray_result_2)=c("Condensation","Other infiltrates","Normal")
levels(data$x_ray_2_reported_by___1)=c("Unchecked","Checked")
levels(data$x_ray_2_reported_by___2)=c("Unchecked","Checked")
levels(data$x_ray_2_reported_by___3)=c("Unchecked","Checked")
levels(data$x_ray_2_result_ext)=c("Condensation","Other infiltrates","Normal")
levels(data$xray_result_3)=c("Condensation","Other infiltrates","Normal")
levels(data$x_ray_3_reported_by___1)=c("Unchecked","Checked")
levels(data$x_ray_3_reported_by___2)=c("Unchecked","Checked")
levels(data$x_ray_3_reported_by___3)=c("Unchecked","Checked")
levels(data$x_ray_3_result_ext)=c("Condensation","Other infiltrates","Normal")
levels(data$cardiac_img)=c("Yes","No","Unknown")
levels(data$radiology_complete)=c("Incomplete","Unverified","Complete")
levels(data$oro_fluids)=c("Yes","No","Unknown")
levels(data$iv_fluids)=c("Yes","No","Unknown")
levels(data$antiviral_cmyn)=c("Yes","No","Unknown")
levels(data$antiviral_cmtrt___1)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___2)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___3)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___4)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___5)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___6)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___7)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___8)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___10)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___11)=c("Unchecked","Checked")
levels(data$antiviral_cmtrt___9)=c("Unchecked","Checked")
levels(data$antibiotic_cmyn)=c("Yes","No","Unknown")
levels(data$iv_ab)=c("Yes","No","Data unavailable")
levels(data$type_iv_ab___0)=c("Unchecked","Checked")
levels(data$type_iv_ab___1)=c("Unchecked","Checked")
levels(data$type_iv_ab___2)=c("Unchecked","Checked")
levels(data$type_iv_ab___3)=c("Unchecked","Checked")
levels(data$type_iv_ab___4)=c("Unchecked","Checked")
levels(data$type_iv_ab___5)=c("Unchecked","Checked")
levels(data$type_iv_ab___6)=c("Unchecked","Checked")
levels(data$type_iv_ab___9)=c("Unchecked","Checked")
levels(data$type_iv_ab___8)=c("Unchecked","Checked")
levels(data$type_iv_ab___7)=c("Unchecked","Checked")
levels(data$o_ab)=c("Yes","No")
levels(data$type_o_ab___1)=c("Unchecked","Checked")
levels(data$type_o_ab___2)=c("Unchecked","Checked")
levels(data$type_o_ab___3)=c("Unchecked","Checked")
levels(data$type_o_ab___4)=c("Unchecked","Checked")
levels(data$type_o_ab___5)=c("Unchecked","Checked")
levels(data$type_o_ab___6)=c("Unchecked","Checked")
levels(data$type_o_ab___7)=c("Unchecked","Checked")
levels(data$type_o_ab___8)=c("Unchecked","Checked")
levels(data$corticost_cmyn)=c("Yes","No","Unknown")
levels(data$corticost_cmroute)=c("Oral","Intravenous","Inhaled")
levels(data$anti_inflammatory___1)=c("Unchecked","Checked")
levels(data$anti_inflammatory___2)=c("Unchecked","Checked")
levels(data$other_anti_inflammatory)=c("Yes","No","Unknown")
levels(data$iv_imglob)=c("Yes","No","Unknown")
levels(data$imod)=c("Yes","No","Unknown")
levels(data$sys_anticoag)=c("Yes","No","Unknown")
levels(data$anti_mal)=c("Yes","No","Unknown")
levels(data$antifung_cmyn)=c("Yes","No","Unknown")
levels(data$experimental)=c("Yes","No","Unknown")
levels(data$other_sc2_treatments)=c("Yes","No","Unknown")
levels(data$vasopressors)=c("Yes","No","Unknown")
levels(data$vasopressors_type___1)=c("Unchecked","Checked")
levels(data$vasopressors_type___2)=c("Unchecked","Checked")
levels(data$vasopressors_type___3)=c("Unchecked","Checked")
levels(data$vasopressors_type___4)=c("Unchecked","Checked")
levels(data$vasopressors_type___5)=c("Unchecked","Checked")
levels(data$vasopressors_type___6)=c("Unchecked","Checked")
levels(data$ecmo)=c("Yes","No","Unknown")
levels(data$blood_trans)=c("Yes","No","Unknown")
levels(data$medication_complete)=c("Incomplete","Unverified","Complete")
levels(data$dsterm)=c("Discharged alive (not hospitalized)","Discharged alive after hospitalization","Transfer to other facility","Death","Palliative discharge","Currently hospitalized","Unknown","Excluded")
levels(data$excluded_reason)=c("Not fulfilled inclusion criteria","Withdrawal of consent","Other")
levels(data$final_dx_1)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
levels(data$related_1)=c("Related","Unclear")
levels(data$final_dx_2)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
levels(data$related_2)=c("Related","Not Related","Unclear")
levels(data$final_dx_3)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
levels(data$final_dx_4)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
levels(data$final_dx_5)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
levels(data$final_dx_6)=c("Abdominal pain","Abscess","Acquired Hemolytic Anaemia","Adenitis","Appendicitis / Peritonitis","Asthma flare","Asymptomatic","Asymptomatic infection","Bacteriemia","Bronchiolitis","Bronchitis","Dehydration","Diabetic debut","Fever without a source","Flu-like syndrome","Gastroenteritis","Gastroenteritis (other)","Hematemesis","Hepatitis","HFH","Hypertension","Inflammatory syndrome","Jaundice","Kawasaki","Kidney stone","Liver failure","Mastoiditis","Neoplasm","Nephritis syndrome","Pneumonia","Psychiatric admission","Pyelonephritis","Salmonellosis","Seizures","Sepsis","Skin/mucosae problems","Social admission","Thrombosis","Trauma","URTI","UTI","Whooping cough","Immunosuppression","Chronic disease","Admission for observation due to unspecified risk","Neonate","Shock")
levels(data$related_3)=c("Related","Not Related","Unclear")
levels(data$outcome_complete)=c("Incomplete","Unverified","Complete")
levels(data$spirometry_complete)=c("Incomplete","Unverified","Complete")
levels(data$fever_ws)=c("Yes","No")
levels(data$lumbar_punc)=c("Yes","No")
levels(data$csf_bacteria)=c("Positive","Negative")
levels(data$csf_vhs)=c("Positive","Negative","Not performed")
levels(data$csf_enterovirus)=c("Positive","Negative","Not performed")
levels(data$csf_sarscov2)=c("Positive","Negative","Not performed")
levels(data$urine_collection)=c("Catheter","Tapping / spontaneus","Perineal bag","Puncture","Urine collection not performed")
levels(data$urine_dipstik)=c("Leucocytes","Nitrites","Leucocytes + Nitrites","Normal","Not performed")
levels(data$urine_culture)=c("Positive","Negative","Not performed")
levels(data$fever_without_source_study_complete)=c("Incomplete","Unverified","Complete")
levels(data$qc_stage)=c("Not started","Clinical quality control performed, waiting for answers to clinical queries","Clinical queries resolved, pending data quality control","Data quality control performed, waiting for answers to data queries","Quality control completed")
levels(data$first_analysis)=c("Yes","No")
levels(data$quality_control_complete)=c("Incomplete","Unverified","Complete")
#
##Arreglar formato de variables fecha:
#
# fechas <- data %>% select(contains("date"))
data$admission_date %<>% ymd()
data$patient_birth_date %<>% ymd()
data$fever_start_date %<>%ymd()
data$pcr_cov2_1_date %<>% ymd()
data$pcr_cov2_2_date %<>% ymd()
data$pcr_cov2_3_date %<>% ymd()
data$pcr_cov2_4_date %<>% ymd()
data$first_sr_sc2_date %<>% ymd()
data$second_sr_sc2_date %<>% ymd()
data$date_ser_1 %<>% ymd()
data$date_ser_2 %<>% ymd()
data$fever_end_date %<>% ymd()
data$oxigen_start_date %<>% ymd()
data$oxigen_end_date %<>% ymd()
data$hft_start_date %<>% ymd()
data$hft_end_date %<>% ymd()
data$cpap_start_date %<>% ymd()
data$cpap_end_date %<>% ymd()
data$picu_admission_date %<>% ymd()
data$picu_discharge_date %<>% ymd()
data$nimv_start_date %<>% ymd()
data$nimv_end_date %<>% ymd()
data$imv_start_date %<>% ymd()
data$imv_end_date %<>% ymd()
data$discharge_date %<>% ymd()
data$x_ray_1_date %<>% ymd()
data$x_ray_2_date %<>% ymd()
data$x_ray_3_date %<>% ymd()
data$lung_ct_date %<>% ymd()
data$iv_ab_start_date %<>% ymd()
data$iv_ab_end_date %<>% ymd()
data$o_ab_start_date %<>% ymd()
data$o_ab_end_date %<>% ymd()
data$qc_date %<>% ymd()
#
```



### Registros por hospital 
 
```{r cars}
print(freq(data$hospital), method = 'render')
```


### Pacientes por edad

```{r}
#data %<>%
  #mutate(age_years = age_months/12)
#data$age_months
#data$age_years


#data[,ageGroup:=cut(age_years,
                        #breaks=c(0,1,3,7,12,18),
                        #include.lowest=TRUE,
                        #labels=c("menores de 1 año","1-2 años","3-6 años","7-11","12-18"))]
#data[,table(ageGroup)]

#ageGroup <- cut2(data$age_years, c(1,3,7,12,18))
#table(ageGroup)
```


### Variables continuas

```{r, echo=FALSE}
#Pasar variables a numericas: 
#Demographics
data$age_months%<>%as.numeric()
#Anamnesis
data$fever_days%<>%as.numeric()
data$fever_days_total%<>%as.numeric()
#Anthropometry
data$weight %<>% as.numeric()
data$weight_percentile%<>% as.numeric()
data$size%<>% as.numeric()
data$size_percentile%<>% as.numeric()
#Admission signs and symptoms
data$temp_vsorres%<>%as.numeric()
data$hr_vsorres%<>%as.numeric()
data$rr_vsorres%<>%as.numeric()
data$sysbp_vsorres%<>%as.numeric()
data$admission_diabp_vsorres%<>%as.numeric()
data$oxy_vsorres%<>%as.numeric()
data$muac%<>%as.numeric()
#Blood tests
data$hb%<>%as.numeric()
data$leukocytes%<>%as.numeric()
data$neutrophils%<>%as.numeric()
data$lymphocytes%<>%as.numeric()
data$platelets%<>%as.numeric()
data$aptt_aptr%<>%as.numeric()
data$pt%<>%as.numeric()
data$inr%<>%as.numeric()
data$fibrino%<>%as.numeric()
data$c_reactive_protein%<>%as.numeric()
data$procalcitonin%<>%as.numeric()
data$cpk%<>%as.numeric()
data$alt_gpt%<>%as.numeric()
data$ast_got%<>%as.numeric()
data$urea%<>%as.numeric()
data$creatinin%<>%as.numeric()
data$ldh%<>%as.numeric()
data$albumin%<>%as.numeric()
data$sodium%<>%as.numeric()
data$d_dimer%<>%as.numeric()
data$il_6%<>%as.numeric()
data$ferritin%<>%as.numeric()
data$trig%<>%as.numeric()
data$bilirubin%<>%as.numeric()
data$lactate%<>%as.numeric()
data$ph%<>%as.numeric()
data$po2%<>%as.numeric()
data$pco2%<>%as.numeric()
#Blood Microbiology
data$sr_sc2_days%<>%as.numeric()
#Pleural Fluid Microbiology
data$ph_thoracentesis%<>%as.numeric()
#Evolution
data$oxygen_therapy_time%<>%as.numeric()
data$hft_time%<>%as.numeric()
data$cpap_time%<>%as.numeric()
data$picu_time%<>%as.numeric()
data$imv_time%<>%as.numeric()
data$nimv_time%<>%as.numeric()
data$hosp_time%<>%as.numeric()
#Complications
data$cardio_comp_bnp%<>%as.numeric()
data$cardio_comp_trop%<>%as.numeric()
#Medication
data$antiviral_days%<>%as.numeric()
data$iv_ab_days%<>%as.numeric()
data$o_ab_days%<>%as.numeric()
data$iv_imglob_dose%<>%as.numeric()
data$iv_imglob_days%<>%as.numeric()
#Fever without source study-lumbar tap and urine
data$csf_leuco%<>%as.numeric()
data$csf_neutro%<>%as.numeric()
data$csf_lympho%<>%as.numeric()
data$protein_csf%<>%as.numeric()
data$glucose_csf%<>%as.numeric()
```

```{r, echo=FALSE}
#Filtrar para solo quedarme con las columnas numericas
numericas <- unlist(lapply(data, is.numeric)) 
num <- data[,numericas]
```

```{r, echo=TRUE}
print(descr(num), method = 'render', table.classes = 'st-small')
```

### Variables demográficas

```{r pressure, echo=FALSE}

demograficas <- data[,c("age_months", "sex", "last_15")]

dfSummary(demograficas, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

#Distribución de la edad
fig <- plot_ly(demograficas, y=~age_months, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Age in months")
fig2 <- plot_ly(demograficas, x=~age_months, type="histogram", name="Age in months", width = 900)
subplot(fig, fig2 , margin = 0.05)

```


### Criterios de inclusión

```{r}
pos1 <- which(colnames(data)=="symptoms_epi_travel")
pos2 <- which(colnames(data)=="symptoms_epi_comm")
crit_inclusion <-data[,c(pos1:pos2)]

sapply(crit_inclusion, function(x) (table(x))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

sapply(crit_inclusion, function(x) round(prop.table(table(x)),2)) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

#dfSummary(crit_inclusion, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

data$index_case <- tolower(data$index_case)
```

### Anamnesis

```{r}

anamnesis <-data[,c("fever_days","fever_days_total","fever_3")]

dfSummary(anamnesis, plain.ascii = FALSE, style = "grid", 
         graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

#Distribución de los datos de fever_days y fever_days_total:

fig1 <- plot_ly(anamnesis, y=~fever_days, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Fever days (from start to admission, including start day)") 
fig11 <- plot_ly(anamnesis, x=~fever_days, type="histogram", name="Fever days (from start to admission, including start day)", width = 1200)

fig2 <- plot_ly(anamnesis, y=~fever_days_total, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Fever days (from start to end, including start day)")
fig22 <-plot_ly(anamnesis, x=~fever_days_total, type="histogram", name="Fever days (from start to end, including start day)", width = 1200)

subplot(fig1, fig11, fig2, fig22, nrows=2, margin = 0.05, widths = c(0.4, 0.6))

```

### Comorbilidades

```{r}
pos1 <- which(colnames(data)=="chroniccard_mhyn")
pos2 <- which(colnames(data)=="other_mhyn")
pos3 <- which(colnames(data)=="immunosupressors")
comorbilidades<-data[,c(pos1:pos2)]

print(freq(data$comorb), method = 'render')

sapply(comorbilidades, function(x) (table(x))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

sapply(comorbilidades, function(x) (round(prop.table(table(x)),2))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

print(freq(data$immunosupressors), method = 'render')

print(freq(data$smoking_mhyn), , method = 'render')

#dfSummary(comorbilidades, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")



```

### Vacunas

```{r}
vacunas<-data[,c("influenza_full_regimen","apsc_vcageind")]
dfSummary(vacunas, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
```

### Antropometría

```{r}

antrop<-data[,c("weight","size")]
#dfSummary(antrop, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
print(descr(antrop), method = 'render', table.classes = 'st-small')

fig1 <- plot_ly(antrop, y=~weight, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Peso en gramos") 
fig1
fig2 <- plot_ly(antrop, y=~size, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Talla en cm")
fig2
subplot(fig1,fig2, shareY=FALSE)

```

### Signos y síntomas de admisión 

```{r}
pos1 <- which(colnames(data)=="temp_vsorres")
pos2 <- which(colnames(data)=="sens_alt")
sig_sint<-data[,c(pos1:pos2)]
sig_sint_num <- sig_sint[,c(1:7)]
sig_sint_cat_iguales <- sig_sint[,c(9:41)]
print(descr(sig_sint_num), method = 'render', table.classes = 'st-small')


fig1 <- plot_ly(sig_sint, y=~temp_vsorres, type="box", boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Temperatura °C", width = 1200, height = 800) 
fig2 <- plot_ly(sig_sint, y=~hr_vsorres, type="box", boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Latidos por minuto", width = 1200, height = 800)
fig3 <- plot_ly(sig_sint, y=~rr_vsorres, type="box", boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Respiraciones por minuto", width = 1200, height = 800) 
fig4 <- plot_ly(sig_sint, y=~sysbp_vsorres, type="box", boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Presión sistólica mmHg", width = 1200, height = 800) 
fig5 <- plot_ly(sig_sint, y=~admission_diabp_vsorres, type="box", boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Presión diastólica mmHg", width = 1200, height = 800) 
fig6 <- plot_ly(sig_sint, y=~oxy_vsorres, type="box", boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Saturación oxígeno %", width = 1200, height = 800) 
#fig7 <- plot_ly(sig_sint, y=~muac, type="box", boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Circunferencia del brazo medio superior mm", width = 1000, height = 600) 

subplot(fig1,fig2,fig3,fig4,fig5,fig6, nrows=2)

print(freq(sig_sint$dehydr), method = 'render')

sapply(sig_sint_cat_iguales, function(x) (table(x))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

sapply(sig_sint_cat_iguales, function(x) (round(prop.table(table(x)),2))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

#dfSummary(sig_sint, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
```

### Examenes de sangre

```{r}
pos1 <- which(colnames(data)=="hb")
pos2 <- which(colnames(data)=="pco2")
sangre<-data[,c(pos1:pos2)]

print(descr(sangre), method = 'render', table.classes = 'st-small')

fig1 <- plot_ly(data, y=~hb, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Hemoglobina g/dL", width = 1200, height = 800)
fig2 <- plot_ly(data, y=~leukocytes, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="leukocytes mm3", width = 1200, height = 800)
fig3 <- plot_ly(data, y=~neutrophils, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="neutrophils mm3", width = 1200, height = 800)
fig4 <- plot_ly(data, y=~lymphocytes, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="lymphocytes mm3", width = 1200, height = 800)
fig5 <- plot_ly(data, y=~platelets, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="platelets mm3", width = 1200, height = 800)
fig6 <- plot_ly(data, y=~aptt_aptr, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="APTT", width = 1200, height = 800)
fig7 <- plot_ly(data, y=~pt, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="PT seg", width = 1200, height = 800)
fig8 <- plot_ly(data, y=~inr, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="inr", width = 1200, height = 800)
fig9 <- plot_ly(data, y=~fibrino, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Fibrinogen g/L", width = 1200, height = 800)
fig10 <- plot_ly(data, y=~c_reactive_protein, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="C-reactive protein mg/L", width = 1200, height = 800)
fig11 <- plot_ly(data, y=~procalcitonin, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Procalcitonin ng/mL", width = 1200, height = 800)
fig12 <- plot_ly(data, y=~cpk, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="cpk mg/dL", width = 1200, height = 800)
fig13 <- plot_ly(data, y=~alt_gpt, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Alanine aminotransferase-GPT U/L", width = 1200, height = 800)
fig14 <- plot_ly(data, y=~ast_got, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Aspartate aminotransferase-GOT U/L", width = 1200, height = 800)
fig15 <- plot_ly(data, y=~urea, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="urea mg/dl", width = 1200, height = 800)
fig16 <- plot_ly(data, y=~creatinin, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Creatinine mg/dl", width = 1200, height = 800)
fig17 <- plot_ly(data, y=~ldh, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Lactate dehydrogenase U/L", width = 1200, height = 800)
fig18 <- plot_ly(data, y=~albumin, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Albumin g/dL", width = 1200, height = 800)
fig19 <- plot_ly(data, y=~sodium, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Serum sodium mmol/L", width = 1200, height = 800)
fig20 <- plot_ly(data, y=~d_dimer, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="D-dimer ug/L", width = 1200, height = 800)
fig21 <- plot_ly(data, y=~il_6, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="IL-6 pg/mL", width = 1200, height = 800)
fig22 <- plot_ly(data, y=~ferritin, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Ferritin ng/mL", width = 1200, height = 800)
fig23 <- plot_ly(data, y=~trig, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Trigiceridos mg/dL", width = 1200, height = 800)
fig24 <- plot_ly(data, y=~bilirubin, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Total bilirubin umol/L", width = 1200, height = 800)
fig25 <- plot_ly(data, y=~lactate, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Lactate mmol/L", width = 1200, height = 800)
fig26 <- plot_ly(data, y=~ph, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="ph", width = 1200, height = 800)
fig27 <- plot_ly(data, y=~po2, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="pO2", width = 1200, height = 800)
fig28 <- plot_ly(data, y=~pco2, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="pcO2", width = 1200, height = 800)

subplot(fig1,fig2,fig3,fig4,fig5,fig6,fig7,fig8,fig9,fig10,fig11,fig12,fig13,fig14,fig15,fig16,fig17,fig18,fig19,fig20,fig21,fig22,fig23,fig24,fig25,fig26,fig27,fig28, nrows=4)

#dfSummary(sangre, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
```

### Microbiología de la secreción respiratoria

```{r}

print(freq(data$pcr_cov2_1), method = 'render')

print(freq(data$virus_obtained_pcr_16), method = 'render')
pos1 <- which(colnames(data)=="virus_obtained_pcr_16")
pos2 <- which(colnames(data)=="pcr_types_virus_sr___16")
virus_pcr_16 <- data[,c(pos1:pos2)]
virus_pcr_16 <- filter(virus_pcr_16,virus_obtained_pcr_16=="Yes")
virus_pcr_16 <- virus_pcr_16[,-1]
dfSummary(virus_pcr_16, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

print(freq(data$pcr_atipical_sr), method = 'render')
pos1 <- which(colnames(data)=="pcr_atipical_sr")
pos2 <- which(colnames(data)=="pcr_bordetella_sr")
pcr_atipical_sr <- data[,c(pos1:pos2)]
pcr_atipical_sr <- filter(pcr_atipical_sr,pcr_atipical_sr=="Yes")
pcr_atipical_sr <- pcr_atipical_sr[,-1]
dfSummary(pcr_atipical_sr, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

print(freq(data$anti_influenza), method = 'render')
print(freq(data$anti_rsv), method = 'render')
print(freq(data$res_samples), method = 'render')

```

### Blood Microbiology

```{r}
#Acute phase serology SARS-CoV-2 performed
print(freq(data$first_sr_sc2), method = 'render')
pos1 <- which(colnames(data)=="first_sr_sc2")
pos2 <- which(colnames(data)=="igg_sc2_1")
first_sr_sc2 <- data[,c(pos1:pos2)]
first_sr_sc2 <- filter(first_sr_sc2,first_sr_sc2=="Yes")
first_sr_sc2 <- first_sr_sc2[,-1]
dfSummary(first_sr_sc2, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")


###----------------Follow-up serology SARS-CoV-2 performed = Todos NO
#print(freq(data$second_sr_sc2), method = 'render')
#pos1 <- which(colnames(data)=="second_sr_sc2")
#pos2 <- which(colnames(data)=="sr_sc2_days")
#second_sr_sc2 <- data[,c(pos1:pos2)]
#second_sr_sc2 <- filter(second_sr_sc2,second_sr_sc2=="Yes")
#second_sr_sc2 <- second_sr_sc2[,-1]
#dfSummary(second_sr_sc2, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
###-----------------

#Blood culture
print(freq(data$blood_culture), method = 'render')
pos1 <- which(colnames(data)=="blood_culture")
pos2 <- which(colnames(data)=="probable_text_2")
blood_culture <- data[,c(pos1:pos2)]
blood_culture <- filter(blood_culture,blood_culture=="Yes")
blood_culture <- blood_culture[,-1]
dfSummary(blood_culture, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

######---------------------------------first_sr_atipical: todos No
#print(freq(data$first_sr_atipical), method = 'render')
#pos1 <- which(colnames(data)=="first_sr_atipical")
#pos2 <- which(colnames(data)=="title1_igg_cn")
#first_sr_atipical <- data[,c(pos1:pos2)]
#first_sr_atipical <- filter(first_sr_atipical,first_sr_atipical=="Yes")
#first_sr_atipical <- first_sr_atipical[,-1]
#dfSummary(first_sr_atipical, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
######----------------------


######---------------------------------second_sr_atipical
#print(freq(data$second_sr_atipical), method = 'render')
#pos1 <- which(colnames(data)=="second_sr_atipical")
#pos2 <- which(colnames(data)=="eroconversion_mn")
#second_sr_atipical <- data[,c(pos1:pos2)]
#second_sr_atipical <- filter(second_sr_atipical,second_sr_atipical=="Yes")
#second_sr_atipical <- second_sr_atipical[,-1]
#dfSummary(second_sr_atipical, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
######---------------------------------

#Blood samples
print(freq(data$blood_samples), method = 'render')

#Plasma samples
print(freq(data$plasma_samples), method = 'render')


```

### Codetección
```{r}
#Codetection
print(freq(data$codetection), method = 'render')
print(freq(data$codetecion_type), method = 'render')
```

### Pleural Fluid Microbiology

```{r}
print(freq(data$thoracentesis_done), method = 'render')
```

### Evolution

```{r}

#Variables de Oxygentherapy
print(freq(data$oxygen_therapy), method = 'render')
print(descr(data$oxygen_therapy_time), method = 'render', table.classes = 'st-small')

#Variables de hft
print(freq(data$hft), method = 'render')
print(descr(data$hft_time), method = 'render', table.classes = 'st-small')

#Variables cpap
print(freq(data$cpap), method = 'render')
print(descr(data$cpap_time), method = 'render', table.classes = 'st-small')

#Variables picu-admission
print(freq(data$picu_admission), method = 'render')
picu_admission <- filter(data,picu_admission=="Yes")
print(descr(picu_admission$picu_time), method = 'render', table.classes = 'st-small')
print(freq(picu_admission$mechanical_ventilation), method = 'render')

#Variables mechanical ventilation:
mechanical_ventilation <- filter(data,mechanical_ventilation=="Yes")
print(freq(mechanical_ventilation$nimv), method = 'render')
print(descr(mechanical_ventilation$nimv_time), method = 'render')
print(freq(mechanical_ventilation$imv), method = 'render')
print(descr(mechanical_ventilation$imv_time), method = 'render')

#Días en hospital:
print(descr(data$hosp_time), method = 'render')

#Graficos de # de días 
fig1 <- plot_ly(data, y=~oxygen_therapy_time, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of oxygen therapy", width = 1200, height = 800)
fig2 <- plot_ly(data, y=~hft_time, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of high flow therapy", width = 1200, height = 800)
fig3 <- plot_ly(data, y=~cpap_time, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of CPAP", width = 1200, height = 800)
fig4 <- plot_ly(data, y=~picu_time, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of PICU admission", width = 1200, height = 800)
fig5 <- plot_ly(data, y=~nimv_time, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of noninvasive mechanical ventilation", width = 1200, height = 800)
fig6 <- plot_ly(data, y=~imv_time, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of invasive mechanical ventilation", width = 1200, height = 800)
fig7 <- plot_ly(data, y=~hosp_time, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of admission", width = 1200, height = 800)

subplot(fig1,fig2,fig3,fig4,fig5,fig6,fig7, nrows = 2)

```

### Complicaciones

```{r}
#Frecuencia de complicaciones
complicaciones <- data[,c("complications","pleural_effusion","pneumatocele_abscess","pneumothorax","cardio_comp","sepsis","renal_failure","kawa","other_complications")]
complicaciones$other_complications <- tolower(complicaciones$other_complications)
print(freq(complicaciones$complications), method = 'render')
compl_yes <- filter(complicaciones,complications=="Yes")
compl_yes <- compl_yes[,-1]
dfSummary(compl_yes, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")


#Detalles de complicación por pleural effusion //Pleural drainage sólo se responde si effusion type = Complicated //drainage type  sólo se responde si Pleural drainage == Yes
pleural_effusion <- filter(data,pleural_effusion=="Yes")
pos1 <- which(colnames(pleural_effusion)=="effusion_type")
pos2 <- which(colnames(pleural_effusion)=="drainage_type")
pleural_effusion <- pleural_effusion[,c(pos1:pos2)]
dfSummary(pleural_effusion, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")


#Detalles de complicion cardiovascular
cardio_comp <- filter(data,cardio_comp=="Yes")
cardio_comp$cardio_comp_other <- tolower(cardio_comp$cardio_comp_other)
pos1 <- which(colnames(cardio_comp)=="cardio_comp_myoc")
pos2 <- which(colnames(cardio_comp)=="cardio_comp_other")
cardio_comp <- cardio_comp[,c(pos1:pos2)]
dfSummary(cardio_comp, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")


```

### Radiología

```{r}
#Resultados de radiografias
radiologia <- data[,c("xray_result_1", "x_ray_1_result_ext", "xray_result_2","x_ray_2_result_ext","xray_result_3", "x_ray_3_result_ext")]
sapply(radiologia, function(x) (table(x))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

sapply(radiologia, function(x) (round(prop.table(table(x)),2))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

#Cardiac imaging
print(freq(data$cardiac_img), method = 'render')
data$card_img_results <- tolower(data$card_img_results)
print(freq(data$card_img_results), method = 'render')

#dfSummary(radiologia, plain.ascii = FALSE, style = "grid", 
          #graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
#with(radiologia, 
     #print(ctable(x = xray_result_1, y = x_ray_1_result_ext, prop = 'n',
                  #totals = T, headings = FALSE),
           #method = "render"))
#with(radiologia, 
     #print(ctable(x = xray_result_2, y = x_ray_2_result_ext, prop = 'n',
                  #totals = T, headings = FALSE),
           #method = "render"))
#with(radiologia, 
     #print(ctable(x = xray_result_3, y = x_ray_3_result_ext, prop = 'n',
                  #totals = T, headings = FALSE),
           #method = "render"))
```

### Medication

```{r}

#Medicamentos principales: "Yes", "No", "Unknown"
medication <- data[,c("oro_fluids", "iv_fluids","antiviral_cmyn","antibiotic_cmyn","corticost_cmyn","iv_imglob","sys_anticoag","anti_mal","antifung_cmyn","experimental","other_sc2_treatments","vasopressors","ecmo","blood_trans")]

sapply(medication, function(x) (table(x))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

sapply(medication, function(x) (round(prop.table(table(x)),2))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))


#Detalles antibioticos:
antibiotic_cmyn <- filter(data,antibiotic_cmyn=="Yes")
antibiotic_cmyn <- antibiotic_cmyn[,c("iv_ab","o_ab")]
dfSummary(antibiotic_cmyn, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")


#Detalles iv_ab:
data$other_iv_ab <- tolower(data$other_iv_ab)
iv_ab <- filter(data,iv_ab=="Yes")
iv_ab_igual <- iv_ab[,c("type_iv_ab___0","type_iv_ab___1","type_iv_ab___2","type_iv_ab___3","type_iv_ab___4","type_iv_ab___5","type_iv_ab___6","type_iv_ab___9","type_iv_ab___8","type_iv_ab___7")]
sapply(iv_ab_igual, function(x) (table(x))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

sapply(iv_ab_igual, function(x) (round(prop.table(table(x)),2))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

#other_iv_ab si se marca la opción 7 de iv
print(freq(iv_ab$other_iv_ab), method = 'render')
print(descr(iv_ab$iv_ab_days), method = 'render')

#Detalles o_ab:
data$other_o_ab <- tolower(data$other_o_ab)
o_ab <- filter(data,o_ab=="Yes")
o_ab_igual <- o_ab[,c("type_o_ab___1","type_o_ab___2","type_o_ab___3","type_o_ab___4","type_o_ab___5","type_o_ab___6","type_o_ab___7","type_o_ab___8")]
sapply(o_ab_igual, function(x) (table(x))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

sapply(o_ab_igual, function(x) (round(prop.table(table(x)),2))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
#other_o_ab si se marca la opicón 8 de o_ab
print(freq(o_ab$other_o_ab), method = 'render')
print(descr(o_ab$o_ab_days), method = 'render')


#Detalles corticosteroides:
data$corticost_cmtrt <- tolower(data$corticost_cmtrt)
data$corticost_cmdose <- tolower(data$corticost_cmdose)

corticost_cmyn <- filter(data,corticost_cmyn=="Yes")
corticost_cmyn <-corticost_cmyn[,c("corticost_cmtrt","corticost_cmdose","corticost_cmroute")]
print(freq(corticost_cmyn), method = 'render')

#Detalles iv_imglob:
iv_imglob <- filter(data,iv_imglob=="Yes")
iv_imglob <-iv_imglob[,c("iv_imglob_dose","iv_imglob_days")]
print(descr(iv_imglob), method = 'render')

#Detalles immunomodulators:
data$imod_type <- tolower(data$imod_type)
imod <- filter(data,imod=="Yes")
imod <- imod[,c("imod_type")]
print(freq(imod), method = 'render')

#Detalles system anticoagulation:
data$sys_anticoag_type <- tolower(data$sys_anticoag_type)
sys_anticoag <- filter(data,sys_anticoag=="Yes")
sys_anticoag <- sys_anticoag[,c("sys_anticoag_type")]
print(freq(sys_anticoag), method = 'render')

#Detalles Agente antimalaria:
data$anti_mal_type <- tolower(data$anti_mal_type)
anti_mal <- filter(data,anti_mal=="Yes")
anti_mal <- anti_mal[,c("anti_mal_type")]
print(freq(anti_mal), method = 'render')

#Detalles Agente antifungico:
data$antifung_type <- tolower(data$antifung_type)
antifung_cmyn <- filter(data,antifung_cmyn=="Yes")
antifung_cmyn <- antifung_cmyn[,c("antifung_type")]
print(freq(antifung_cmyn), method = 'render')


#Detalles Agente experimental:
data$experimental_type <- tolower(data$experimental_type)
experimental <- filter(data,experimental=="Yes")
experimental <- experimental[,c("experimental_type")]
print(freq(experimental), method = 'render')

#Detalles: Otros medicamentos para curar COVID-19
data$other_sc2_treatments_text <- tolower(data$other_sc2_treatments_text)
other_sc2_treatments <- filter(data,other_sc2_treatments=="Yes")
other_sc2_treatments <- other_sc2_treatments[,c("other_sc2_treatments_text")]
print(freq(other_sc2_treatments), method = 'render')

#Detalles vasopressores 
vasopressors <- filter(data,vasopressors=="Yes")
vasopressors <- vasopressors[,c("vasopressors_type___1","vasopressors_type___2","vasopressors_type___3","vasopressors_type___4","vasopressors_type___5","vasopressors_type___6")]
sapply(vasopressors, function(x) (table(x))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

sapply(vasopressors, function(x) (round(prop.table(table(x)),2))) %>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

#Tratamiento anti-inflamatorio:
data$other_anti_inflammatory_type <- tolower(data$other_anti_inflammatory_type)
anti_inflamatory <- data[,c("anti_inflammatory___1","anti_inflammatory___2","other_anti_inflammatory")]
dfSummary(anti_inflamatory, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
print(freq(data$other_anti_inflammatory_type), method = 'render')


medication <- data[,c("oro_fluids", "iv_fluids", "antiviral_cmyn", "antiviral_cmtrt___1", "antiviral_cmtrt___2", "antiviral_cmtrt___3","antiviral_cmtrt___4", "antiviral_cmtrt___5","antiviral_cmtrt___6","antiviral_cmtrt___7","antiviral_cmtrt___8","antiviral_cmtrt___10","antiviral_cmtrt___11","antiviral_cmtrt___9","antiviral_days","antibiotic_cmyn","iv_ab","type_iv_ab___0","type_iv_ab___1","type_iv_ab___2","type_iv_ab___3","type_iv_ab___4","type_iv_ab___5","type_iv_ab___6","type_iv_ab___9","type_iv_ab___8","type_iv_ab___7","iv_ab_days", "o_ab","type_o_ab___1","type_o_ab___2","type_o_ab___3","type_o_ab___4","type_o_ab___5","type_o_ab___6","type_o_ab___7","type_o_ab___8","o_ab_days","corticost_cmyn","corticost_cmroute","anti_inflammatory___1","anti_inflammatory___2","other_anti_inflammatory","iv_imglob","iv_imglob_days","imod","sys_anticoag","anti_mal","antifung_cmyn","experimental","other_sc2_treatments","vasopressors","vasopressors_type___1","vasopressors_type___2","vasopressors_type___3","vasopressors_type___4","vasopressors_type___5","vasopressors_type___6","ecmo","blood_trans")]


#Graficos:
fig1 <- plot_ly(data, y=~iv_ab_days, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of intravenous antibiotic", width = 1200, height = 800)
fig2 <- plot_ly(data, y=~o_ab_days, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of oral antibiotic", width = 1200, height = 800)
fig3 <- plot_ly(data, y=~iv_imglob_dose, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Daily intravenous immune globulin dose", width = 1200, height = 800)
fig4 <- plot_ly(data, y=~iv_imglob_days, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of intravenous immune globulin treatment", width = 1200, height = 800)

subplot(fig1,fig2,fig3,fig4)
```

### Outcome

```{r}
#Patient outcome: 
print(freq(data$dsterm), method = 'render')
print(freq(data$excluded_reason), method = 'render')
data$dsterm_other_text <- tolower(data$dsterm_other_text)
print(freq(data$dsterm_other_text), method = 'render')
#data$final_dx_global_concept <- tolower(data$final_dx_global_concept)
data$final_dx_global_concept <- tolower(data$final_dx_global_concept)
#print(freq(data$final_dx_global_concept), method = 'render')
data$final_dx_global_concept <- toupper(data$final_dx_global_code)
print(freq(data$final_dx_global_code), method = 'render')

outcome <- data[,c("final_dx_1","final_dx_2","final_dx_3")]
print((freq(outcome, order = "freq")), method = 'render')

```

```{r}
# final_dx_1 <- outcome%>% group_by(final_dx_1) %>% summarise(n=n())
# final_dx_2 <- outcome%>% group_by(final_dx_2) %>% summarise(n=n())
# final_dx_3 <- outcome%>% group_by(final_dx_3) %>% summarise(n=n())
# 
# fig1 <- plot_ly(final_dx_1, y = ~reorder(final_dx_1,n), x = ~n, type = 'bar', name = 'Primary diagnosis related to COVID-19',orientation = 'h',width = 600, height = 1800) %>% layout(legend = list(orientation = "h",   # show entries horizontally
#                      xanchor = "center",  # use center of legend as anchor
#                      x = 0.5))             # put legend in center of x-axis
# fig2 <- plot_ly(final_dx_2, y = ~reorder(final_dx_2,n), x = ~n, type = 'bar', name = 'Secondary diagnosis: comorbidity which conditioned this admission',orientation = 'h',width = 600, height = 1800)%>% layout(legend = list(orientation = "h",   # show entries horizontally
#                      xanchor = "center",  # use center of legend as anchor
#                      x = 0.5))             # put legend in center of x-axis
# fig3 <- plot_ly(final_dx_3, y = ~reorder(final_dx_3,n), x = ~n, type = 'bar', name = 'Other diagnosis',orientation = 'h',width = 600, height = 1600)%>% layout(legend = list(orientation = "h",   # show entries horizontally
#                      xanchor = "center",  # use center of legend as anchor
#                      x = 0.5))             # put legend in center of x-axis
# fig1
# fig2
# fig3

# outcome_1 <- data[,c("final_dx_1","related_1")]
# outcome_2 <- data[,c("final_dx_2","related_2")]
# outcome_3 <- data[,c("final_dx_3","related_3")]
# 
# outcome_1$Related <- ifelse(outcome_1$related_1 == 'Related', 1, 0)
# outcome_1$Not_Related <- ifelse(outcome_1$related_1 == 'Not Related', 1, 0)
# outcome_1$Unclear <- ifelse(outcome_1$related_1 == 'Unclear', 1, 0)
# outcome_1$Not_specified <- ifelse(is.na(outcome_1$related_1), 1, 0)
# 
# 
# outcome_2$Related <- ifelse(outcome_2$related_2 == 'Related', 1, 0)
# outcome_2$Not_Related <- ifelse(outcome_2$related_2 == 'Not Related', 1, 0)
# outcome_2$Unclear <- ifelse(outcome_2$related_2 == 'Unclear', 1, 0)
# outcome_2$Not_specified <- ifelse(is.na(outcome_2$related_2), 1, 0)
# 
# outcome_3$Related <- ifelse(outcome_3$related_3 == 'Related', 1, 0)
# outcome_3$Not_Related <- ifelse(outcome_3$related_3 == 'Not Related', 1, 0)
# outcome_3$Unclear <- ifelse(outcome_3$related_3 == 'Unclear', 1, 0)
# outcome_3$Not_specified <- ifelse(is.na(outcome_3$related_3), 1, 0)
# 
# 
# final_dx_1 <- outcome_1 %>% group_by(final_dx_1) %>% summarise(n=n(), 
#                                                                Related=sum(Related),
#                                                                Not_Related=sum(Not_Related),
#                                                                Unclear=sum(Unclear),
#                                                                Not_specified=sum(Not_specified))
# final_dx_2 <- outcome_2 %>% group_by(final_dx_2) %>% summarise(n=n(), 
#                                                                Related=sum(Related),
#                                                                Not_Related=sum(Not_Related),
#                                                                Unclear=sum(Unclear),
#                                                                Not_specified=sum(Not_specified))
# final_dx_3 <- outcome_3 %>% group_by(final_dx_3) %>% summarise(n=n(), 
#                                                                Related=sum(Related),
#                                                                Not_Related=sum(Not_Related),
#                                                                Unclear=sum(Unclear),
#                                                                Not_specified=sum(Not_specified))
# 
# 
# 
# fig1 <- plot_ly(final_dx_1, x = ~final_dx_1, y = ~Related, type = 'bar', name = 'Related',width = 1200, height = 600)
# fig1 <- fig1 %>% add_trace(y = ~Not_Related, name = 'Not_Related')
# fig1 <- fig1 %>% add_trace(y = ~Unclear, name = 'Unclear')
# fig1 <- fig1 %>% add_trace(y = ~Not_specified, name = 'Not_specified')
# fig1 <- fig1 %>% layout(yaxis = list(title = 'Count'), barmode = 'stack')
# fig1
# 
# 
# fig2 <- plot_ly(final_dx_2, x = ~final_dx_2, y = ~Related, type = 'bar', name = 'Related',width = 1200, height = 600)
# fig2 <- fig2 %>% add_trace(y = ~Not_Related, name = 'Not_Related')
# fig2 <- fig2 %>% add_trace(y = ~Unclear, name = 'Unclear')
# fig2<- fig2 %>% add_trace(y = ~Not_specified, name = 'Not_specified')
# fig2 <- fig2 %>% layout(yaxis = list(title = 'Count'), barmode = 'stack')
# fig2
# 
# fig3 <- plot_ly(final_dx_3, x = ~final_dx_3, y = ~Related, type = 'bar', name = 'Related',width = 1200, height = 600)
# fig3 <- fig3 %>% add_trace(y = ~Not_Related, name = 'Not_Related')
# fig3 <- fig3 %>% add_trace(y = ~Unclear, name = 'Unclear')
# fig3<- fig3 %>% add_trace(y = ~Not_specified, name = 'Not_specified')
# fig3 <- fig3 %>% layout(yaxis = list(title = 'Count'), barmode = 'stack')
# fig3
```

### Fever without source study-lumbar tap and urine

```{r}
fever_ws <- data[,c("fever_ws","lumbar_punc","urine_collection")]
dfSummary(fever_ws, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

#Lumbar puncture
data$csf_baceria_type<-tolower(data$csf_baceria_type)
lumbar_punc <- filter(data,lumbar_punc=="Yes")
lumbar_punc <- lumbar_punc[,c("csf_bacteria","csf_baceria_type","csf_vhs","csf_enterovirus","csf_sarscov2","csf_leuco","csf_neutro","csf_lympho","protein_csf","glucose_csf")]
dfSummary(lumbar_punc, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

#Urine collection
urine_collection <- filter(data,urine_collection !="Urine collection not performed")
urine_collection <- urine_collection[,c("urine_dipstik","urine_culture")]
dfSummary(urine_collection, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

#Urine culture == Positive:
data$bacteria_urine <- tolower(data$bacteria_urine)
urine_culture <- filter(data,urine_culture !="Positive")
urine_culture <- urine_culture[,c("bacteria_urine")]
dfSummary(urine_culture, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")

#Graficos de # de días 
fig1 <- plot_ly(data, y=~csf_leuco, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Leucocytes in CSF mm3", width = 1200, height = 800)
fig2 <- plot_ly(data, y=~csf_neutro, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Percentage of Neutrophils CSF%", width = 1200, height = 800)
fig3 <- plot_ly(data, y=~csf_lympho, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Percentage of Lymphocytes in CSF %", width = 1200, height = 800)
fig4 <- plot_ly(data, y=~protein_csf, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Protein in CSF mg/dl", width = 1200, height = 800)
fig5 <- plot_ly(data, y=~glucose_csf, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Glucose in CSF g/dl", width = 1200, height = 800)
fig6 <- plot_ly(data, y=~imv_time, type="box",boxpoints = "all", jitter = 0.4,pointpos = -1.8, name="Days of invasive mechanical ventilation", width = 1200, height = 800)
subplot(fig1,fig2,fig3,fig4,fig5,fig6, nrows = 2) 

```

